---
title: "Process_SolisensePigmentsData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_SolisensePigmentsData.Rmd processes and combines BalticPhotoperiod_Imported_SolisenseDarkafterLight.Rds and BalticPhotoperiod_Imported_SolisenseLight.Rds from Data/ImportedData/ImportedSolisenseData folder. This .Rmd generates BalticPhotoperiod_Processed_SolisenseData.Rds (stored in Data/ProcessedData/ProcessedSolisenseData folder), plots stored in Output/Figures folder, and tables stored in Output/TablesRds folder.

# Load Libraries and set Project Variables

```{r load libraries, warning = FALSE, echo=FALSE} 
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(caret)
library(reshape2)
library(gcookbook)
library(scales)
library(Cairo) #for greek symbols
library(googledrive)
library(googlesheets4)
library(readxl)
library(multcompView)
```

```{r set project variables}
Project <- "BalticPhotoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisenseData")
DataIn <- file.path("..", "Data", "ImportedData", "ImportedSolisenseData", fsep = .Platform$file.sep)

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
```

# List and read Imported_Solisense RDS

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

# This RDS contained only data from corresponding growth light 
# Also, conteined mean sig - mean for replica measured on the same day

```{r read ProcessFile Sol}
SolisenseFile <- "../Data/ImportedData/ImportedSolisenseData/BalticPhotoperiod_Imported_SolisenseLight.Rds"  

SolisenseFileName <- str_split(string = SolisenseFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")

SolFits <- readRDS(SolisenseFile)  %>%
  ungroup()
```

# This RDS contained only sigma in 1s of dark after corresponding light (it caused problems when I tried to combain them with sig in the light)
# Also, conteined mean for sig1s - mean for replica measured on the same day

```{r read ProcessFile Sol1s}
# Solisense1sFile <- "../Data/ImportedData/ImportedSolisenseData/BalticPhotoperiod_Imported_SolisenseDarkafterLight.Rds"
# 
# Solisense1sFileName <- str_split(string = Solisense1sFile, "/")[[1]][3] %>%
#   str_remove(pattern = ".Rds")
# 
# SolFits1s <- readRDS(Solisense1sFile)  %>%
#   ungroup()
```


```{r Preparing df for further analysis}
SolFits <-SolFits %>% 
  select(c(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, MC, Tube, O2, WL, LightShape, ExpEndDate, PARPhotonDose_day, FilenameSolisense, ObsDate, ObsTime, ObsDateTime, Ex_WL, ActPAR, LR_s, nm445, nm590, nm445Corr, nm590Corr, ActPARCorr, Sig, Sig_nm2psii, Sigdark, Sigdark_nm2psii, ActPARCorr_photonsm2s, FoOxbo, qpOxbo,  JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRqpOxbo_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig, E_days, Time_h)) %>% 
  filter(Strain=="BA127R"| Strain=="BA48R"| Strain=="BA56G"| Strain=="BA77G") %>% 
  filter(WL=="WW") %>% 
  filter(O2==21) %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 
SolFits$facetsPhotonDose_day = factor(SolFits$WL, labels = c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"))
SolFits$facetsExcitation = factor(SolFits$WL, labels = c("Excitation~(nm)"))
SolFits$facetsStrain = factor(SolFits$WL, labels = c("Strain"))


# SolFits1s <-SolFits1s %>% 
#   select(c(SampleID, Run, Strain, ExpDate, Par_ue, Photoperiod, MC, Tube, O2, WL, LightShape, ExpEndDate, PARPhotonDose_day, FilenameSolisense, ObsDate, ObsTime, Ex_WL, ActPAR, LR_s, nm445, nm590, nm445Corr, nm590Corr, ActPARCorr, Sig1s, Sig1s_nm2psii, ActPARCorr_photonsm2s, E_days, Time_h)) %>% 
#   filter(Strain=="BA127R"| Strain=="BA48R"| Strain=="BA56G"| Strain=="BA77G") %>% 
#   filter(WL=="WW") %>% 
#   filter(O2==21) %>% 
#   mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
#          Strain=="BA48R"~"PE-rich_048",
#         Strain=="BA56G"~"PC-rich_056",
#          Strain=="BA77G"~"PC-rich_077")) 
# SolFits1s$facetsPhotonDose_day = factor(SolFits1s$WL, labels = c("PAR~photon~dose~(µmol~photons~m^{-2}~d^{-1})"))
# SolFits1s$facetsExcitation = factor(SolFits1s$WL, labels = c("Excitation~(nm)"))
# SolFits1s$facetsStrain = factor(SolFits1s$WL, labels = c("Strain"))
```

# Filter unrevelant data and outliers

```{r filter outliers}
# #Filter one unrevelant data point at 445nm, 16h, 900uE
SolFitsAll445<-SolFits %>%
  filter(Ex_WL == 445) %>%
  filter(Sig<250) 
SolFitsAll590<-SolFits %>%
  filter(Ex_WL == 590)
SolFits<-rbind(SolFitsAll445,SolFitsAll590)
  rm(SolFitsAll445,SolFitsAll590)
  
# SolFitsAll4451s<-SolFits1s %>%
#   filter(Ex_WL == 445) %>%
#   filter(Sig1s<250) 
# SolFitsAll5901s<-SolFits1s %>%
#   filter(Ex_WL == 590)
# SolFits1s<-rbind(SolFitsAll4451s,SolFitsAll5901s)
#   rm(SolFitsAll4451s,SolFitsAll5901s)  
```

# Create preliminary plots 

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFits %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = Sig, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  facet_grid(rows = vars(Ex_WL), cols = vars(Photoperiod)) +
  theme_bw()
```

# Load tmaxAG catalog and create 4 df for vertical lines (coloured as Strain) contained tMaxAG values

```{r}
gs4_deauth()
tmaxAG<- read_sheet("https://docs.google.com/spreadsheets/d/1ksY7xlg9wOsICOBRmZkHPKdd9KOislNwPDzyuJ3UIUI/edit#gid=0")
as.data.frame(tmaxAG)
tmaxAG <- tmaxAG

tmaxAG<-tmaxAG %>% 
  mutate(Par_ue = as.numeric(Par_ue)) %>%
  mutate(Photoperiod = as.numeric(Photoperiod)) %>%
  mutate(tMaxAG = as.numeric(tMaxAG)) %>%
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077"))
```

```{r select revelant columns}
tMaxAGLines_056<-tmaxAG %>% 
  filter(Strain == "PC-rich_056") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_077<-tmaxAG %>% 
  filter(Strain == "PC-rich_077") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_048<-tmaxAG %>% 
  filter(Strain == "PE-rich_048") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
tMaxAGLines_127<-tmaxAG %>% 
  filter(Strain == "PE-rich_127") %>% 
  select(c(Par_ue, Photoperiod, tMaxAG)) %>% 
  unique()
```

# Choose only exp data for sigma and JVPSII in the corresponding light

```{r choose only exp data}
O1 <- SolFits %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 600 | Par_ue == 900) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 4)

O2 <- SolFits %>%
  filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days < 9)

O3 <- SolFits %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 4)

O4 <- SolFits %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days <= 14)

O5 <- SolFits %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=14)
  
O6 <- SolFits %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 8) %>% 
  filter(E_days <=14)

O7 <- SolFits %>%
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 12) %>% 
  filter(E_days <=10)

O8 <- SolFits %>%
  filter(Par_ue == 180 | Par_ue == 300) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=10)

O9 <- SolFits %>%
  filter(Par_ue == 900) %>% 
  filter(Photoperiod == 8 | Photoperiod == 12) %>% 
  filter(E_days <=7)

O10 <- SolFits %>%
  filter(Par_ue == 30) %>% 
  filter(Photoperiod == 24) %>% 
  filter(E_days <= 8)

SolFitsExp <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)
```


# Choose only Stationary data for sigma and JVPSII in the corresponding light

```{r choose only St data}
O1 <- SolFits %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 600 | Par_ue == 900) %>%
  filter(Photoperiod == 24) %>%
  filter(E_days > 4)

O2 <- SolFits %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >14)
  
O3 <- SolFits %>%
  filter(Par_ue == 90) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O4 <- SolFits %>%
  filter(Par_ue == 180 | Par_ue == 300) %>%
  filter(Photoperiod == 8 | Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O5 <- SolFits %>%
  filter(Par_ue == 900 | Par_ue == 600) %>% 
  filter(Photoperiod == 8 | Photoperiod == 16) %>% 
  filter(E_days >7)

SolFitsSt <-rbind(O1, O2, O3, O4, O5)

rm(O1, O2, O3, O4, O5)
```



# Choose only exp data for sigma at 1s after corresponding light

```{r choose only exp data for Sig 1s}
# O1 <- SolFits1s %>%
#   filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 600 | Par_ue == 900) %>% 
#   filter(Photoperiod == 24) %>% 
#   filter(E_days <= 4)
# 
# O2 <- SolFits1s %>%
#   filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>% 
#   filter(Photoperiod == 16) %>% 
#   filter(E_days < 9)
# 
# O3 <- SolFits1s %>%
#   filter(Par_ue == 900 | Par_ue == 600) %>% 
#   filter(Photoperiod == 16) %>% 
#   filter(E_days <= 4)
# 
# O4 <- SolFits1s %>%
#   filter(Par_ue == 30) %>% 
#   filter(Photoperiod == 16) %>% 
#   filter(E_days <= 14)
# 
# O5 <- SolFits1s %>%
#   filter(Par_ue == 30) %>% 
#   filter(Photoperiod == 8 | Photoperiod == 12) %>% 
#   filter(E_days <=14)
#   
# O6 <- SolFits1s %>%
#   filter(Par_ue == 90) %>% 
#   filter(Photoperiod == 8) %>% 
#   filter(E_days <=14)
# 
# O7 <- SolFits1s %>%
#   filter(Par_ue == 90) %>% 
#   filter(Photoperiod == 12) %>% 
#   filter(E_days <=10)
# 
# O8 <- SolFits1s %>%
#   filter(Par_ue == 180 | Par_ue == 300) %>% 
#   filter(Photoperiod == 8 | Photoperiod == 12) %>% 
#   filter(E_days <=10)
# 
# O9 <- SolFits1s %>%
#   filter(Par_ue == 900) %>% 
#   filter(Photoperiod == 8 | Photoperiod == 12) %>% 
#   filter(E_days <=7)
# 
# O10 <- SolFits1s %>%
#   filter(Par_ue == 30) %>% 
#   filter(Photoperiod == 24) %>% 
#   filter(E_days <= 8)
# 
# SolFitsExp1s <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)
# 
# rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)
```


# Choose only Stationary data for sigma at 1s after corresponding light

```{r choose only St data}
# O1 <- SolFits1s %>%
#   filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 600 | Par_ue == 900) %>%
#   filter(Photoperiod == 24) %>%
#   filter(E_days > 4)
# 
# O2 <- SolFits1s %>%
#   filter(Par_ue == 30) %>%
#   filter(Photoperiod == 12 | Photoperiod == 16) %>%
#   filter(E_days >14)
#   
# O3 <- SolFits1s %>%
#   filter(Par_ue == 90) %>%
#   filter(Photoperiod == 12 | Photoperiod == 16) %>%
#   filter(E_days >10)
# 
# O4 <- SolFits1s %>%
#   filter(Par_ue == 180 | Par_ue == 300) %>%
#   filter(Photoperiod == 8 | Photoperiod == 12 | Photoperiod == 16) %>%
#   filter(E_days >10)
# 
# O5 <- SolFits1s %>%
#   filter(Par_ue == 900 | Par_ue == 600) %>% 
#   filter(Photoperiod == 8 | Photoperiod == 16) %>% 
#   filter(E_days >7)
# 
# SolFitsSt1s <-rbind(O1, O2, O3, O4, O5)
# 
# rm(O1, O2, O3, O4, O5)
```


# Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFits %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4") +
  geom_vline(data = tMaxAGLines_077, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1") +
  geom_vline(data = tMaxAGLines_048, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = tMaxAGLines_127, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsExp %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4") +
  geom_vline(data = tMaxAGLines_077, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1") +
  geom_vline(data = tMaxAGLines_048, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = tMaxAGLines_127, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsSt %>%
  ggplot() +
  geom_point(aes(x = Time_h, y = Sig, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  geom_vline(data = tMaxAGLines_056, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown4") +
  geom_vline(data = tMaxAGLines_077, aes(xintercept = tMaxAG), linetype="dotdash", colour = "brown1") +
  geom_vline(data = tMaxAGLines_048, aes(xintercept = tMaxAG), linetype="dotdash", colour = "seagreen4") +
  geom_vline(data = tMaxAGLines_127, aes(xintercept = tMaxAG), linetype="dotdash", colour = "palegreen3") +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
```
# Combine Exp and St data

```{r}
  SolFitsExp$Phase <- 'Exponential'
  # SolFitsExp1s$Phase <- 'Exponential'
  
  SolFitsSt$Phase <- 'Pre-stationary'
  # SolFitsSt1s$Phase <- 'Pre-stationary'
  
  SolFitsExpSt <-rbind(SolFitsExp, SolFitsSt)
  # SolFitsExpSt1s <-rbind(SolFitsExp1s, SolFitsSt1s)
  
  rm(SolFitsExp, SolFitsSt, SolFits)
  #rm(SolFitsExp1s, SolFitsSt1s, SolFits1s)
```

#Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

SolFitsExpSt %>%
  # filter(E_days!=2) %>% 
  filter(Ex_WL==445) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)),  alpha = 0.8, size = 3, show.legend = T) +
  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab2) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3", "goldenrod2", "khaki2"), name="", labels = lab3) +
  ggh4x::facet_nested(cols = vars(Phase), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```

# Calculate Sigma mean from 3 replica measured on the same day
# 6 replica b/c 3 replica * 2 values ("up" and "down")

```{r calculate Sigma mean from 3 replica measured on the same day}
SolFitsExpSt <- SolFitsExpSt %>%
  group_by(SampleID, Ex_WL, ObsDate, Par_ue, Photoperiod, WL, O2, Phase) %>%
  
  summarize(SampleID, Ex_WL, FilenameSolisense, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, Phase,  PARPhotonDose_day, ObsDate, ObsTime, ObsDateTime, Sig, Sig_nm2psii, ActPARCorr_photonsm2s, Sigdark_nm2psii, FoOxbo, qpOxbo, JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRqpOxbo_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig, facetsPhotonDose_day, facetsExcitation, facetsStrain,
            meanSig_nm2psii = mean(Sig_nm2psii),
            sdSig_nm2psii = sd(Sig_nm2psii),
            meanSigdark_nm2psii = mean(Sigdark_nm2psii),
            sdSigdark_nm2psii = sd(Sigdark_nm2psii)) %>%
  ungroup()

SolFitsExpSt<- SolFitsExpSt %>%
group_by(SampleID) %>%
  arrange(ObsDate) %>%
  mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
ungroup()

SolFitsExpSt<- SolFitsExpSt %>%
  mutate(Time_h = E_days*24)
```

# Calculate Sigma1s mean from 3 replica measured on the same day
# 6 replica b/c 3 replica * 2 values ("up" and "down")

```{r calculate Sigma1s mean from 3 replica measured on the same day}
# SolFitsExpSt1s <- SolFitsExpSt1s %>%
#   group_by(SampleID, Ex_WL, ObsDate, Par_ue, Photoperiod, WL, O2, Phase) %>%
#   
#   summarize(SampleID, Ex_WL, FilenameSolisense, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, Phase,  PARPhotonDose_day, ObsDate, ObsTime, Sig1s, Sig1s_nm2psii, ActPARCorr_photonsm2s, facetsPhotonDose_day, facetsExcitation, facetsStrain,
#             meanSig1s_nm2psii = mean(Sig1s_nm2psii),
#             sdSig1s_nm2psii = sd(Sig1s_nm2psii)) %>%
#   ungroup()
# 
# SolFitsExpSt1s<- SolFitsExpSt1s %>%
# group_by(SampleID) %>%
#   arrange(ObsDate) %>%
#   mutate(E_days = as.numeric((ObsDate - ExpDate[1]))) %>%
# ungroup()
# 
# SolFitsExpSt1s<- SolFitsExpSt1s %>%
#   mutate(Time_h = E_days*24)
```

Make "one big - All" mean to combine all days (divided by Exp and St) and all replica when samples were measured 
(This give me only one value of JVPSII for further growth vs JVPSII plot and sig plot as well)


# Calculate Sigma mean from all data measured on Exp or St phase 
# Usually Allmean contains 12 replica - two different days of measurements * 3 replica * 2 values (up and down)

```{r calculate Sigma mean from exp phase}

SolFitsExpSt<-SolFitsExpSt %>% 
  group_by(Strain, Ex_WL, Par_ue, Photoperiod, WL, O2, Phase) %>%
  
  summarize(SampleID, Ex_WL, FilenameSolisense, Run, Strain, ExpDate, Par_ue, Photoperiod, O2, WL, Phase,  PARPhotonDose_day, ObsDate, ObsTime, ObsDateTime, Sig, Sig_nm2psii, meanSig_nm2psii, sdSig_nm2psii, ActPARCorr_photonsm2s, Sigdark_nm2psii, meanSigdark_nm2psii, sdSigdark_nm2psii, FoOxbo, qpOxbo, JVPSII_aLHIIOxbomax, JVPSII_ETRtauav_FoSig, JVPSII_ETRqpOxbo_FoSig, JVPSII_ETRtauav_aLHII_Sig, JVPSII_ETRqpOxbo_aLHII_Sig, facetsPhotonDose_day, facetsExcitation, facetsStrain, E_days, Time_h,
              
            AllmeanJVPSII_aLHIIOxbomax= mean(JVPSII_aLHIIOxbomax),
            AllmeanJVPSII_ETRtauav_FoSig= mean(JVPSII_ETRtauav_FoSig),
            AllmeanJVPSII_ETRqpOxbo_FoSig= mean(JVPSII_ETRqpOxbo_FoSig),
            AllmeanJVPSII_ETRtauav_aLHII_Sig = mean(JVPSII_ETRtauav_aLHII_Sig),
            AllmeanJVPSII_ETRqpOxbo_aLHII_Sig= mean(JVPSII_ETRqpOxbo_aLHII_Sig),
            AllmeanSig_nm2psii = mean(Sig_nm2psii),
            AllsdSig_nm2psii = sd(Sig_nm2psii),
            AllmeanSigdark_nm2psii = mean(Sigdark_nm2psii),
            AllsdSigdark_nm2psii = sd(Sigdark_nm2psii)) %>%
  ungroup()
```

# Filter otliers to calculate exponential decay function

```{r filter outliers (5 data points from Exp)}

Sol7<-SolFitsExpSt %>% 
  filter(Ex_WL==445) 

Sol3<-SolFitsExpSt %>% #keeping all data except <180 (one data point)
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue !=900) %>% 
  filter(Strain=="PC-rich_056") %>% 
  filter(Sig>180)
Sol6<-SolFitsExpSt %>% # keeping all except 2 data points
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue ==900) %>% 
  filter(Strain=="PC-rich_056") 

Sol8<-SolFitsExpSt %>% 
  filter(Phase == "Pre-stationary") %>% 
  filter(Strain=="PC-rich_056") %>% 
  filter(Par_ue ==900 | Par_ue ==600) %>% 
  filter(Sig<230)

Sol9<-SolFitsExpSt %>% 
  filter(Phase == "Pre-stationary") %>% 
  filter(Strain=="PC-rich_056") %>% 
  filter(Par_ue !=900 & Par_ue !=600) %>% 
  filter(Sig>130)

#BA127
Sol4<-SolFitsExpSt %>% #removing one data point
  filter(Phase == "Exponential") %>%
  filter(Ex_WL==590) %>%
  filter(Par_ue ==30) %>%
  filter(Strain=="PE-rich_127") %>%
  filter(Sig>310)
Sol5<-SolFitsExpSt %>%
  filter(Phase == "Exponential") %>% #removing 3 data points
  filter(Ex_WL==590) %>%
  filter(Par_ue ==300 | Par_ue ==180 | Par_ue ==90) %>%
  filter(Strain=="PE-rich_127") %>%
  filter(Sig>200)
Sol16<-SolFitsExpSt %>% # keeping all except 2 data points
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue ==900 | Par_ue ==600) %>% 
  filter(Strain=="PE-rich_127")  %>% 
  filter(Sig<520)
Sol12<-SolFitsExpSt %>% 
  filter(Phase == "Pre-stationary") %>% 
  filter(Strain=="PE-rich_127")

#BA48
Sol1<-SolFitsExpSt %>% #keeping all data
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue !=900) %>% 
  filter(Strain=="PE-rich_048") 
Sol15<-SolFitsExpSt %>% # removing 2 data points
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue ==900 | Par_ue ==600) %>% 
  filter(Strain=="PE-rich_048") %>% 
  filter(Sig<520) 
Sol10<-SolFitsExpSt %>% # removing few data points
  filter(Phase == "Pre-stationary") %>% 
  filter(Par_ue !=900) %>% 
  filter(Strain=="PE-rich_048") %>% 
  filter(Sig>290)
Sol11<-SolFitsExpSt %>% #keeping all data
  filter(Phase == "Pre-stationary") %>%
  filter(Par_ue ==900) %>%
  filter(Strain=="PE-rich_048")


#BA77
Sol2<-SolFitsExpSt %>% #keeping all data
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue !=900) %>% 
  filter(Strain=="PC-rich_077") 
Sol13<-SolFitsExpSt %>% #keeping all data
  filter(Phase == "Pre-stationary") %>% 
  filter(Strain=="PC-rich_077") %>% 
  filter(Par_ue != 600)  
  #filter(Sig<490)
Sol14<-SolFitsExpSt %>% #filter 1 data point
  filter(Phase == "Pre-stationary") %>% 
  filter(Strain=="PC-rich_077") %>% 
  filter(Par_ue==600) %>% 
  filter(Sig<250)
Sol17<-SolFitsExpSt %>% # removing 2 data points
  filter(Phase == "Exponential") %>% 
  filter(Ex_WL==590) %>% 
  filter(Par_ue ==900 | Par_ue ==600) %>% 
  filter(Strain=="PC-rich_077") %>% 
  filter(Sig<520) 

SolFitsExpFitAll<-rbind(Sol1, Sol2, Sol3, Sol4, Sol5, Sol6, Sol7, Sol8, Sol9, Sol10, Sol11, Sol12, Sol13, Sol14, Sol15, Sol16, Sol17)

rm(Sol1, Sol2, Sol3, Sol4, Sol5, Sol6, Sol7, Sol8, Sol9, Sol10, Sol11, Sol12, Sol13, Sol14, Sol15, Sol16, Sol17)


SolFitsExpFitAll_1<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential") 
SolFitsExpFitAll_2<-SolFitsExpFitAll %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Strain=="PC-rich_056" | Strain=="PC-rich_077") %>%
  filter(Par_ue!=90)
SolFitsExpFitAll_3<-SolFitsExpFitAll %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Strain=="PE-rich_048" | Strain=="PE-rich_127") 

SolFitsExpFitAll<-rbind(SolFitsExpFitAll_1, SolFitsExpFitAll_2, SolFitsExpFitAll_3)

```

# Create plot to check data before and after filtering outliers

```{r checking data before and after filtering outliers}
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

SolFitsExpSt %>% 
  filter(Ex_WL == 590) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3",  "goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Phase), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 


SolFitsExpFitAll %>% 
  filter(Ex_WL == 590) %>% 
  ggplot() +
  geom_point(aes(x = PARPhotonDose_day, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3",  "goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Phase), rows = vars(Strain), labeller = label_parsed) +
  theme_bw() 
```

# Fit the data to exponential decays

```{r fit the data to exponential decays, echo=FALSE, warning = FALSE}
 SolFitsExpFitAll$facetsPhase <- "Phase~of~growth"
 SolFitsExpFitAll$facetsStrain <- "Strain"
 
SolFitsExpFit590Clean <-SolFitsExpFitAll %>% 
  drop_na(Sig_nm2psii) %>%
  filter(Ex_WL == 590) %>% 
  select(c(Sig_nm2psii, PARPhotonDose_day, Strain, Phase, facetsPhase, facetsStrain)) 

# Fit the data
fitted590 <- SolFitsExpFit590Clean %>% 
  nest(-c(Strain, Phase, facetsPhase, facetsStrain)) %>%
  mutate(
    fit = map(data, possibly(~nls(Sig_nm2psii ~ SSasymp(PARPhotonDose_day, yf, y0, log_alpha), data = .))),
    tidied = map(fit, tidy),
    augmented590 = map(fit, augment))

# Produce a table of fit parameters: y0, yf, alpha
fitted_Param590<-fitted590 %>% 
  unnest(tidied) %>% 
  select(Strain, Phase, term, estimate) %>% 
pivot_wider(., names_from = c(term), values_from = c(estimate)) %>% 
  mutate(alpha = exp(log_alpha))
```

```{r unnest, preparing df to preparing final plot, echo=FALSE, warning = FALSE}
augmented590<-fitted590  %>%
  unnest(augmented590) %>%
  select(c(Strain, Phase, facetsPhase, facetsStrain, PARPhotonDose_day,Sig_nm2psii, .fitted)) 
```

# Create Sigma plot at 590

```{r create Sigma plot, fig.height = 8, fig.width = 8, warning = FALSE}

k_data056 = data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain  = c("Strain"), Strain  = c("PC-rich_056"))
k_data077 = data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain  = c("Strain"), Strain  = c("PC-rich_077"))
k_data048 = data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain  = c("Strain"), Strain  = c("PE-rich_048"))
k_data127 = data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain  = c("Strain"), Strain  = c("PE-rich_127"))

data_text_y0Exp<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('y0 = 7.4', 'y0 = 5.9', 'y0 = 8.5', 'y0 = 7.9'))
data_text_yfExp<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('yf = 3.3', 'yf = 1.9', 'yf = 4.4', 'yf = 3.7'))
data_text_lambdaExp<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('    \u03BB = 3.6e-07', '    \u03BB = 3.1e-07', '    \u03BB = 2.4e-07', '    \u03BB = 3.3e-07'))

data_text_y0St<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c(' y0 = 20.8', 'y0 = 9.8', 'y0 = 8.8', 'y0 = 9.5'))
data_text_yfSt<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('yf = 1.7', 'yf = 1.4', 'yf = 3.0', 'yf = 2.3'))
data_text_lambdaSt<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('    \u03BB = 1.3e-06', '    \u03BB = 5.3e-07', '    \u03BB = 5.5e-07', '    \u03BB = 6.6e-07'))

# data_text_AnovaExp<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, b', ' ANOVA, \u03B1 = 0.05, ab'))
# data_text_AnovaSt<- data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, b', ' ANOVA, \u03B1 = 0.05, bc', 'ANOVA, \u03B1 = 0.05, d'))

data_text_AnovaExp56<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056"),  label = c('a'))
data_text_AnovaExp77<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_077"),  label = c("a"))
data_text_AnovaExp48<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PE-rich_048"),  label = c("b"))
data_text_AnovaExp127<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PE-rich_127"),  label = c("ab"))

data_text_AnovaSt56<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056"),  label = c('a'))
data_text_AnovaSt77<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_077"),  label = c("b"))
data_text_AnovaSt48<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PE-rich_048"),  label = c("bc"))
data_text_AnovaSt127<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PE-rich_127"),  label = c("d"))

data_text_AnovaExp56P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056"),  label = c('A'))
data_text_AnovaExp77P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_077"),  label = c("A"))
data_text_AnovaExp48P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PE-rich_048"),  label = c("A"))
data_text_AnovaExp127P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PE-rich_127"),  label = c("A"))

data_text_AnovaSt56P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056"),  label = c('B'))
data_text_AnovaSt77P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_077"),  label = c("B"))
data_text_AnovaSt48P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PE-rich_048"),  label = c("A"))
data_text_AnovaSt127P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PE-rich_127"),  label = c("B"))


data_text_AnovaPhase<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('ANOVA, \u03B1 = 0.05', 'ANOVA, \u03B1 = 0.05', 'ANOVA, \u03B1 = 0.05', 'ANOVA, \u03B1 = 0.05'))



# WL.labs <- c("Phase of growth")
# names(WL.labs) <- c("WW")
# O2.labs <- c("Strain")
# names(O2.labs) <- c(21)

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

SolFitsExpFitAll590<-SolFitsExpFitAll %>% 
  filter(Ex_WL==590) 

ggplot(SolFitsExpFitAll590, aes(x = PARPhotonDose_day, y = Sig_nm2psii)) +
  geom_point(aes(x = PARPhotonDose_day, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = T) +
  geom_point(aes(x = PARPhotonDose_day, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, show.legend = F) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue)), width=0, size=0.3, show.legend = F) +
  geom_line(aes(PARPhotonDose_day, .fitted), colour = "blue", linetype = "solid", size = 0.3, show.legend = F, augmented590) +
  geom_text(data=data_text_y0Exp, aes(x=70000000, y=10, label=label), size=3.5) +
  geom_text(data=data_text_yfExp, aes(x=70000000, y=8.5, label=label), size=3.5) +
  #geom_text(data=data_text_lambdaExp, aes(x=70000000, y=7, label=label), size=3.5) +

  geom_text(data=data_text_y0St, aes(x=7500000, y=10, label=label), size=3.5) +
  geom_text(data=data_text_yfSt, aes(x=7500000, y=8.5, label=label), size=3.5) +
  #geom_text(data=data_text_lambdaSt, aes(x=7500000, y=7, label=label), size=3.5) +
  

  
  geom_text(data=data_text_AnovaExp56, aes(x=75000000, y=4.6, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp77, aes(x=75000000, y=3.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp48, aes(x=75000000, y=5.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp127, aes(x=75000000, y=5, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaSt56, aes(x=75000000, y=3.2, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt77, aes(x=75000000, y=3.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt48, aes(x=75000000, y=4.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt127, aes(x=75000000, y=4, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaExp56P, aes(x=75000000, y=1.6, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp77P, aes(x=75000000, y=0.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp48P, aes(x=75000000, y=2.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp127P, aes(x=75000000, y=2, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaSt56P, aes(x=75000000, y=0.2, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt77P, aes(x=75000000, y=0.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt48P, aes(x=75000000, y=1.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt127P, aes(x=75000000, y=1, label=label), colour = "blue", size=4) +
  
  geom_text(data=data_text_AnovaPhase, aes(x=24000000, y=-0.8, label=label), colour = "blue", size=4) +
  
  geom_segment(data = k_data056, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "seagreen4", size = 6, alpha = 0.7) +
  geom_segment(data = k_data077, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "palegreen3", size = 6, alpha = 0.7) +
  geom_segment(data = k_data048, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown1", size = 6, alpha = 0.7) +
  geom_segment(data = k_data127, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown4", size = 6, alpha = 0.7) +
  
  
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3",  "goldenrod2", "khaki2"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Cumulative diel PAR ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(breaks=seq(0, 80000000, by = 30000000), label=scientific_10) +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(xlim = c(0, 90000000), ylim = c(-2, 12)) +
  
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  #ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(WL, Phase), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.85,0.88),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        legend.title = element_blank(),
        legend.text = element_text(size=11))

```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("Fig_Sigma590",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Create Sigma plot at 590 for merging with sin590pig

```{r create Sigma plot, fig.height = 8, fig.width = 8, warning = FALSE}
data_textA <- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain  = c("Strain"), Strain  = c("PC-rich_056"), label = c('A'))

k_data056 = data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain  = c("Strain"), Strain  = c("PC-rich_056"))
k_data077 = data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain  = c("Strain"), Strain  = c("PC-rich_077"))
k_data048 = data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain  = c("Strain"), Strain  = c("PE-rich_048"))
k_data127 = data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain  = c("Strain"), Strain  = c("PE-rich_127"))


data_text_y0Exp<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('y[0]~"="~7.4', 'y[0]~"="~5.9', 'y[0]~"="~8.5', 'y[0]~"="~7.9'))
data_text_yfExp<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('y[f]~"="~3.3', 'y[f]~"="~1.9', 'y[f]~"="~4.4', 'y[f]~"="~3.7'))
data_text_lambdaExp<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('    \u03BB = 3.6e-07', '    \u03BB = 3.1e-07', '    \u03BB = 2.4e-07', '    \u03BB = 3.3e-07'))

data_text_y0St<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('~~y[0]~"="~20.8', 'y[0]~"="~9.8', 'y[0]~"="~8.8', 'y[0]~"="~9.5'))
data_text_yfSt<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('y[f]~"="~1.7', 'y[f]~"="~1.4', 'y[f]~"="~3.1', 'y[f]~"="~2.3'))
data_text_lambdaSt<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('    \u03BB = 1.3e-06', '    \u03BB = 5.3e-07', '    \u03BB = 5.5e-07', '    \u03BB = 6.6e-07'))

data_text_AnovaExp56<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056"),  label = c('a'))
data_text_AnovaExp77<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_077"),  label = c("a"))
data_text_AnovaExp48<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PE-rich_048"),  label = c("b"))
data_text_AnovaExp127<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PE-rich_127"),  label = c("ab"))

data_text_AnovaSt56<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056"),  label = c('a'))
data_text_AnovaSt77<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_077"),  label = c("b"))
data_text_AnovaSt48<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PE-rich_048"),  label = c("bc"))
data_text_AnovaSt127<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PE-rich_127"),  label = c("d"))

data_text_AnovaExp56P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056"),  label = c('A'))
data_text_AnovaExp77P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_077"),  label = c("A"))
data_text_AnovaExp48P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PE-rich_048"),  label = c("A"))
data_text_AnovaExp127P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PE-rich_127"),  label = c("A"))

data_text_AnovaSt56P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056"),  label = c('B'))
data_text_AnovaSt77P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PC-rich_077"),  label = c("B"))
data_text_AnovaSt48P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PE-rich_048"),  label = c("A"))
data_text_AnovaSt127P<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Pre-stationary"), facetsStrain = c("Strain"), Strain  = c("PE-rich_127"),  label = c("B"))


data_text_AnovaPhase<- data.frame(facetsPhase = c("Phase~of~growth"), Phase = c("Exponential"), facetsStrain = c("Strain"), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('ANOVA, \u03B1 = 0.05', 'ANOVA, \u03B1 = 0.05', 'ANOVA, \u03B1 = 0.05', 'ANOVA, \u03B1 = 0.05'))



# WL.labs <- c("Phase of growth")
# names(WL.labs) <- c("WW")
# O2.labs <- c("Strain")
# names(O2.labs) <- c(21)

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

SolFitsExpFitAll590<-SolFitsExpFitAll %>% 
  filter(Ex_WL==590) 

Soli590A<-ggplot(SolFitsExpFitAll590, aes(x = PARPhotonDose_day, y = Sig_nm2psii)) +
  geom_point(aes(x = PARPhotonDose_day, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = F) +
  geom_point(aes(x = PARPhotonDose_day, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, show.legend = F) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue)), width=0, size=0.3, show.legend = F) +
  geom_line(aes(PARPhotonDose_day, .fitted), colour = "blue", linetype = "solid", size = 0.3, show.legend = F, augmented590) +
  
  geom_text(data=data_text_y0Exp, aes(x=70000000, y=10, label=label), size=4, parse = TRUE) +
  geom_text(data=data_text_yfExp, aes(x=70000000, y=8.5, label=label), size=4, parse = TRUE) +
  #geom_text(data=data_text_lambdaExp, aes(x=70000000, y=7, label=label), size=3.5) +

  geom_text(data=data_text_y0St, aes(x=70000000, y=10, label=label), size=4, parse = TRUE) +
  geom_text(data=data_text_yfSt, aes(x=70000000, y=8.5, label=label), size=4, parse = TRUE) +
  #geom_text(data=data_text_lambdaSt, aes(x=70000000, y=7, label=label), size=3.5) +
  
  geom_text(data=data_text_AnovaExp56, aes(x=75000000, y=4.6, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp77, aes(x=75000000, y=3.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp48, aes(x=75000000, y=5.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp127, aes(x=75000000, y=5, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaSt56, aes(x=75000000, y=3.2, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt77, aes(x=75000000, y=3.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt48, aes(x=75000000, y=4.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt127, aes(x=75000000, y=4, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaExp56P, aes(x=75000000, y=1.6, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp77P, aes(x=75000000, y=0.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp48P, aes(x=75000000, y=2.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp127P, aes(x=75000000, y=2, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaSt56P, aes(x=75000000, y=0.2, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt77P, aes(x=75000000, y=0.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt48P, aes(x=75000000, y=1.5, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt127P, aes(x=75000000, y=1, label=label), colour = "blue", size=4) +
  
  geom_text(data=data_text_AnovaPhase, aes(x=24000000, y=-0.8, label=label), colour = "blue", size=4) +
  geom_text(data=data_textA, aes(x=0.5e07, y=10, label=label), size=6) +
  
  geom_segment(data = k_data056, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "seagreen4", size = 6, alpha = 0.7) +
  geom_segment(data = k_data077, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "palegreen3", size = 6, alpha = 0.7) +
  geom_segment(data = k_data048, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown1", size = 6, alpha = 0.7) +
  geom_segment(data = k_data127, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown4", size = 6, alpha = 0.7) +
  
  
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3",  "goldenrod2", "khaki2"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Cumulative diel PAR ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(breaks=seq(0, 80000000, by = 30000000), label=scientific_10) +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(xlim = c(0, 90000000), ylim = c(-2, 12)) +
  
  ggh4x::facet_nested(cols = vars(facetsPhase, Phase), rows = vars(facetsStrain, Strain), labeller = label_parsed) +
  #ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(WL, Phase), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        strip.background.y = element_blank(),
        strip.text.y = element_blank(),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.85,0.88),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        legend.title = element_blank(),
        legend.text = element_text(size=11))
Soli590A
```



# Calculated Anova and Tukey test from data points

```{r calculated statistics}
SigFit590Stats <-SolFitsExpFitAll %>% 
  filter(Ex_WL == 590) 

SigFit590Stats$Par_ue <- factor(SigFit590Stats$Par_ue)
SigFit590Stats$Photoperiod <- factor(SigFit590Stats$Photoperiod)
SigFit590Stats$Strain <- factor(SigFit590Stats$Strain)
SigFit590Stats$Phase <- factor(SigFit590Stats$Phase)
SigFit590Stats$PARPhotonDose_day <- factor(SigFit590Stats$PARPhotonDose_day)

# Three way Anova with interactions
model<-aov(Sig_nm2psii~PARPhotonDose_day*Phase*Strain, data=SigFit590Stats)
Anova_Sig590<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
#TukeyHSDTest_Sig590<-TukeyHSD(model, which = c("PARPhotonDose_day", "Phase", "Strain"))
```

# Save RDS that create stats and tables

```{r}
saveRDS(Anova_Sig590, file.path(TableRdsPath, paste(Project, "Anova_Sig590.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Calculated Anova and Tukey test from exponential decay parameters

```{r calculated statistics}
Sig590Stats<-fitted_Param590
Sig590Stats2<-rbind(Sig590Stats, Sig590Stats)
Sig590Stats2$Strain <- factor(Sig590Stats2$Strain)
Sig590Stats2$Phase <- factor(Sig590Stats2$Phase)

# Two-way Anova
model<-aov(y0~Strain*Phase, data=Sig590Stats2)
AnovaTest_Sig590_y0<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_Sig590_y0$Parameter <- 'y0'

model<-aov(yf~Strain*Phase, data=Sig590Stats2)
AnovaTest_Sig590_yf<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_Sig590_yf$Parameter <- 'yf'

model<-aov(alpha~Strain*Phase, data=Sig590Stats2)
AnovaTest_Sig590_alpha<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
AnovaTest_Sig590_alpha$Parameter <- 'alpha'

Anova_Sig590_Param<-rbind(AnovaTest_Sig590_y0, AnovaTest_Sig590_yf, AnovaTest_Sig590_alpha)

rm(AnovaTest_Sig590_y0, AnovaTest_Sig590_yf, AnovaTest_Sig590_alpha, Sig590Stats, Sig590Stats2, model)
```

# Save RDS that create stats and tables

```{r}
# saveRDS(Anova_Sig590, file.path(TableRdsPath, paste(Project, "Anova_Sig590.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Exstracting models for each fit

```{r}
fittedmodel<-fitted590  %>%
  select(c(Strain, Phase, fit))
```

# Anova from the model 
(When I made Anova from all models I got a result, but it is not possible to tell, what is sig different. Tukey doesn't work here. That is why I compare each pair of data - models separately)

```{r}
#1->048 Exp
#2->077 Exp
#3->056 Exp
#4->127 Exp
#5->056 St
#6->077 ST
#7->048 St
#8->127 St

#Comparing model for strains from Exp phase
fittedmodelStrainExp<-fittedmodel
  anova056077Exp<-anova(fittedmodelStrainExp[[3]][[2]], fittedmodelStrainExp[[3]][[3]])
  anova056077Exp$FitComparison <- '056_077_Exp'
  anova048127Exp<-anova(fittedmodelStrainExp[[3]][[1]], fittedmodelStrainExp[[3]][[4]])
  anova048127Exp$FitComparison <- '048_127_Exp'
  anova056048Exp<-anova(fittedmodelStrainExp[[3]][[1]], fittedmodelStrainExp[[3]][[3]])
  anova056048Exp$FitComparison <- '056_048_Exp'
  anova077048Exp<-anova(fittedmodelStrainExp[[3]][[1]], fittedmodelStrainExp[[3]][[2]])
  anova077048Exp$FitComparison <- '077_048_Exp'
  anova056127Exp<-anova(fittedmodelStrainExp[[3]][[3]], fittedmodelStrainExp[[3]][[4]])
  anova056127Exp$FitComparison <- '056_127_Exp'
  anova077127Exp<-anova(fittedmodelStrainExp[[3]][[2]], fittedmodelStrainExp[[3]][[4]])
  anova077127Exp$FitComparison <- '077_127_Exp'
  anova_SigModelStrainExp<-rbind(anova056077Exp, anova048127Exp, anova056048Exp, anova077048Exp, anova056127Exp, anova077127Exp)
  anova_SigModelStrainExp <-anova_SigModelStrainExp %>% 
  drop_na(Df) 
  rm(anova056077Exp, anova048127Exp, anova056048Exp, anova077048Exp, anova056127Exp, anova077127Exp)

#Comparing model for strains from St phase
fittedmodelStrainSt<-fittedmodel 
  anova056077St<-anova(fittedmodelStrainSt[[3]][[5]], fittedmodelStrainSt[[3]][[6]])
  anova056077St$FitComparison <- '056_077_St'
  anova048127St<-anova(fittedmodelStrainSt[[3]][[7]], fittedmodelStrainSt[[3]][[8]])
  anova048127St$FitComparison <- '048_127_St'
  anova056048St<-anova(fittedmodelStrainSt[[3]][[5]], fittedmodelStrainSt[[3]][[7]])
  anova056048St$FitComparison <- '056_048_St'
  anova077048St<-anova(fittedmodelStrainSt[[3]][[6]], fittedmodelStrainSt[[3]][[7]])
  anova077048St$FitComparison <- '077_048_St'
  anova056127St<-anova(fittedmodelStrainSt[[3]][[5]], fittedmodelStrainSt[[3]][[8]])
  anova056127St$FitComparison <- '056_127_St'
  anova077127St<-anova(fittedmodelStrainSt[[3]][[6]], fittedmodelStrainSt[[3]][[8]])
  anova077127St$FitComparison <- '077_127_St'
  anova_SigModelStrainSt<-rbind(anova056077St, anova048127St, anova056048St, anova077048St, anova056127St, anova077127St)
  anova_SigModelStrainSt <-anova_SigModelStrainSt %>% 
  drop_na(Df) 
  rm(anova056077St, anova048127St, anova056048St, anova077048St, anova056127St, anova077127St)
  
  
#Comparing model for each strains from different phase (Exp vs St)
fittedmodelPhase<-fittedmodel 
  anova056ExpSt<-anova(fittedmodelPhase[[3]][[3]], fittedmodelPhase[[3]][[5]])
  anova056ExpSt$FitComparison <- '056_Exp_St'
  anova077ExpSt<-anova(fittedmodelPhase[[3]][[2]], fittedmodelPhase[[3]][[6]])
  anova077ExpSt$FitComparison <- '077_Exp_St'
  anova048ExpSt<-anova(fittedmodelPhase[[3]][[1]], fittedmodelPhase[[3]][[7]])
  anova048ExpSt$FitComparison <- '048_Exp_St'
  anova127ExpSt<-anova(fittedmodelPhase[[3]][[4]], fittedmodelPhase[[3]][[8]])
  anova127ExpSt$FitComparison <- '127_Exp_St'
  anova_SigModelPhase<-rbind(anova056ExpSt, anova077ExpSt, anova048ExpSt, anova127ExpSt)
  anova_SigModelPhase <-anova_SigModelPhase %>% 
  drop_na(Df) 
  
  Anova_Sig590_Model<-rbind(anova_SigModelStrainExp, anova_SigModelStrainSt, anova_SigModelPhase)
  
  rm(anova056ExpSt, anova077ExpSt, anova048ExpSt, anova127ExpSt, anova_SigModelStrainExp, anova_SigModelStrainSt, anova_SigModelPhase)
```

# Save RDS that create stats and tables

```{r}
saveRDS(Anova_Sig590_Model, file.path(TableRdsPath, paste(Project, "Anova_Sig590_Model.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Removed unneccessary df from the environment

```{r}
rm(SolFitsExpFit590Clean, fitted_Param590, data_text_lambdaExp, data_text_y0Exp, data_text_yfExp, data_text_lambdaSt, data_text_y0St, data_text_yfSt, fitted590, fittedmodel, fittedmodelPhase, fittedmodelStrainExp, fittedmodelStrainSt, SigFit590Stats, SolFitsExpFitAll590, SolFitsExpFitAll_1, SolFitsExpFitAll_2, SolFitsExpFitAll_3, augmented590)
```

```{r, warning=FALSE}
SolFitsExpFit445Clean <-SolFitsExpFitAll %>% 
  drop_na(Sig_nm2psii) %>%
  filter(Ex_WL == 445) %>% 
  select(c(Sig_nm2psii, PARPhotonDose_day, Strain, Phase, O2, WL)) 

# Fit the data
fitted445 <- SolFitsExpFit445Clean %>% 
  nest(-c(Strain, Phase, O2, WL)) %>%
  mutate(Linear_Model = map(data, ~lm(Sig_nm2psii ~ PARPhotonDose_day, data = .))) %>% 
  mutate(Linear_Model_Param = map(Linear_Model, tidy),          
         Linear_Model_Predict = map(Linear_Model, possibly(augment)),          
         Linear_Model_Glance = map(Linear_Model, possibly(glance)))   

augmented445<-fitted445 %>% 
  unnest(Linear_Model_Predict) %>% 
  select(c(Strain, Phase, O2, WL, PARPhotonDose_day,Sig_nm2psii, .fitted)) 
```

# Create Sigma plot at 445

```{r create Sigma plot, fig.height = 8, fig.width = 8, warning = FALSE}
# data_text_AnovaExp<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, a'))
# data_text_AnovaSt<- data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, a', 'ANOVA, \u03B1 = 0.05, b', 'ANOVA, \u03B1 = 0.05, a'))
# data_text_AnovaPhase<- data.frame(WL = c("WW", "WW"), Phase = c("Pre-stationary"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c("Phase, p > 0.05", 'Phase, p < 0.05', 'Phase, p < 0.05', 'Phase, p < 0.05'))

k_data056 = data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_056"))
k_data077 = data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_077"))
k_data048 = data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_048"))
k_data127 = data.frame(WL = c("WW"),Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_127"))


data_text_AnovaExp56<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PC-rich_056"),  label = c('a'))
data_text_AnovaExp77<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PC-rich_077"),  label = c("a"))
data_text_AnovaExp48<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PE-rich_048"),  label = c("a"))
data_text_AnovaExp127<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PE-rich_127"),  label = c("a"))

data_text_AnovaSt56<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_056"),  label = c('a'))
data_text_AnovaSt77<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_077"),  label = c("a"))
data_text_AnovaSt48<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_048"),  label = c("b"))
data_text_AnovaSt127<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_127"),  label = c("a"))

data_text_AnovaExp56P<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PC-rich_056"),  label = c('A'))
data_text_AnovaExp77P<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PC-rich_077"),  label = c("A"))
data_text_AnovaExp48P<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PE-rich_048"),  label = c("A"))
data_text_AnovaExp127P<- data.frame(WL = c("WW"), Phase = c("Exponential"), O2=c(21), Strain  = c("PE-rich_127"),  label = c("A"))

data_text_AnovaSt56P<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_056"),  label = c('A'))
data_text_AnovaSt77P<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PC-rich_077"),  label = c("B"))
data_text_AnovaSt48P<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_048"),  label = c("B"))
data_text_AnovaSt127P<- data.frame(WL = c("WW"), Phase = c("Pre-stationary"), O2=c(21), Strain  = c("PE-rich_127"),  label = c("B"))

# data_text_AnovaPhase<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('t-test, \u03B1 = 0.05', 't-test, \u03B1 = 0.05', 't-test, \u03B1 = 0.05', 't-test, \u03B1 = 0.05'))

data_text_AnovaPhase<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"), label = c(' , \u03B1 = 0.05', ' , \u03B1 = 0.05', ' , \u03B1 = 0.05', ' , \u03B1 = 0.05'))
data_text_AnovaPhase2<- data.frame(WL = c("WW", "WW"), Phase = c("Exponential"), O2=c(21, 21, 21, 21), Strain  = c("PC-rich_056", "PC-rich_077", "PE-rich_048", "PE-rich_127"),  label = c('italic(t)~-test', 'italic(t)~-test', 'italic(t)~-test', 'italic(t)~-test'))

WL.labs <- c("Phase of growth")
names(WL.labs) <- c("WW")
O2.labs <- c("Strain")
names(O2.labs) <- c(21)

scientific_10 <- function(x) {   parse(text=gsub("e\\+*", " %*% 10^", scales::scientific_format()(x))) }
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

SolFitsExpFitAll445<-SolFitsExpFitAll %>% 
  filter(Ex_WL==445) 

ggplot(SolFitsExpFitAll445, aes(x = PARPhotonDose_day, y = Sig_nm2psii)) +
  geom_point(aes(x = PARPhotonDose_day, y = AllmeanSig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, alpha = 0.8, show.legend = T) +
  geom_point(aes(x = PARPhotonDose_day, y = Sig_nm2psii, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 1, show.legend = F) +
  geom_errorbar(aes(x = PARPhotonDose_day, ymin = AllmeanSig_nm2psii - AllsdSig_nm2psii, ymax = AllmeanSig_nm2psii + AllsdSig_nm2psii, colour=as.factor(Par_ue)), width=0, size=0.3, show.legend = F) +
  geom_line(aes(PARPhotonDose_day, .fitted), colour = "blue", linetype = "solid", size = 0.3, show.legend = F, augmented445) +
  
  geom_text(data=data_text_AnovaExp56, aes(x=75000000, y=3, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp77, aes(x=75000000, y=3.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp48, aes(x=75000000, y=3.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp127, aes(x=75000000, y=3, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaSt56, aes(x=75000000, y=2.7, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt77, aes(x=75000000, y=3.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt48, aes(x=75000000, y=3.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt127, aes(x=75000000, y=2.5, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaExp56P, aes(x=75000000, y=0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp77P, aes(x=75000000, y=0.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp48P, aes(x=75000000, y=0.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaExp127P, aes(x=75000000, y=0, label=label), colour = "blue", size=4) +
    
  geom_text(data=data_text_AnovaSt56P, aes(x=75000000, y=-0.7, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt77P, aes(x=75000000, y=0.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt48P, aes(x=75000000, y=0.0, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaSt127P, aes(x=75000000, y=-0.5, label=label), colour = "blue", size=4) +
  
  #geom_text(data=data_text_AnovaPhase, aes(x=18000000, y=-0.8, label=label), colour = "blue", size=4) +
  
  geom_text(data=data_text_AnovaPhase, aes(x=24500000, y=-0.8, label=label), colour = "blue", size=4) +
  geom_text(data=data_text_AnovaPhase2, aes(x=6500000, y=-0.8, label=label), colour = "blue", size=4, parse = TRUE) +
  
  geom_segment(data = k_data056, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "seagreen4", size = 6, alpha = 0.7) +
  geom_segment(data = k_data077, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "palegreen3", size = 6, alpha = 0.7) +
  geom_segment(data = k_data048, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown1", size = 6, alpha = 0.7) +
  geom_segment(data = k_data127, aes(x =9e07, y = -Inf, xend = 9e07, yend = Inf), color = "brown4", size = 6, alpha = 0.7) +
  
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3",  "goldenrod2", "khaki2"), name="", labels = lab2) +
  labs(y=expression(paste(sigma,""["PSII"]*"' (nm"^"2"*" quanta"^"-1"*")")), x = "Cumulative diel PAR ( µmol photons "~m^-2~""~d^-1~")") +
  scale_x_continuous(breaks=seq(0, 80000000, by = 30000000), label=scientific_10) +
  scale_y_continuous(breaks=seq(0, 10, by = 2)) +
  coord_cartesian(xlim = c(0, 90000000), ylim = c(-2, 12)) +
  ggh4x::facet_nested(rows = vars(O2, Strain), cols = vars(WL, Phase), labeller = labeller(WL = WL.labs, O2 = O2.labs)) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.85,0.88),
        legend.key.height= unit(0.003, 'cm'),
        legend.spacing.y = unit(-0.1, "cm"),
        legend.spacing.x = unit(-0.1, 'cm'),
        legend.title = element_blank(),
        legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_Sigma445",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Calculated Anova and Tukey test from data points

```{r calculated statistics}
SigFit445Stats <-SolFitsExpFitAll %>% 
  filter(Ex_WL == 445) 

SigFit445Stats$Par_ue <- factor(SigFit445Stats$Par_ue)
SigFit445Stats$Photoperiod <- factor(SigFit445Stats$Photoperiod)
SigFit445Stats$Strain <- factor(SigFit445Stats$Strain)
SigFit445Stats$Phase <- factor(SigFit445Stats$Phase)
SigFit445Stats$PARPhotonDose_day <- factor(SigFit445Stats$PARPhotonDose_day)

# Three way Anova with interactions
model<-aov(Sig_nm2psii~PARPhotonDose_day*Phase*Strain, data=SigFit445Stats)
Anova_Sig445<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
#TukeyHSDTest_Sig<-TukeyHSD(model, which = c("PARPhotonDose_day", "Phase", "Strain"))
```

# Save RDS that create stats and tables

```{r}
saveRDS(Anova_Sig445, file.path(TableRdsPath, paste(Project, "Anova_Sig445.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Anova from the linear model 
https://stackoverflow.com/questions/24527116/write-regression-summary-to-the-csv-file-in-r

t-test from the linear model Exp
```{r}
# Exp
Stats56_77Exp<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_056" | Strain == "PC-rich_077") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=Stats56_77Exp)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_56_77Exp<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_56_77Exp$FitComparison <- '056_077_Exp'

SolFits56_48Exp<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_056" | Strain == "PE-rich_048") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits56_48Exp)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_56_48Exp<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_56_48Exp$FitComparison <- '056_048_Exp'

SolFits56_127Exp<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_056" | Strain == "PE-rich_127")  
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits56_127Exp)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_56_127Exp<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_56_127Exp$FitComparison <- '056_127_Exp'

SolFits48_127Exp<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PE-rich_048" | Strain == "PE-rich_127")  
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits48_127Exp)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_48_127Exp<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_48_127Exp$FitComparison <- '048_127_Exp'

SolFits77_48Exp<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_077" | Strain == "PE-rich_048") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits77_48Exp)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_77_48Exp<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_77_48Exp$FitComparison <- '077_048_Exp'

SolFits77_127Exp<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_077" | Strain == "PE-rich_127") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits77_127Exp)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_77_127Exp<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_77_127Exp$FitComparison <- '077_127_Exp'

modelExp<-rbind(model_56_77Exp, model_56_48Exp, model_56_127Exp, model_48_127Exp, model_77_48Exp, model_77_127Exp)
  rm(model_56_77Exp, model_56_48Exp, model_56_127Exp, model_48_127Exp, model_77_48Exp, model_77_127Exp)
```

t-test from the linear model St
```{r}
# Exp
Stats56_77St<-SolFitsExpFitAll %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_056" | Strain == "PC-rich_077") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=Stats56_77St)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_56_77St<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_56_77St$FitComparison <- '056_077_St'

SolFits56_48St<-SolFitsExpFitAll %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_056" | Strain == "PE-rich_048") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits56_48St)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_56_48St<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_56_48St$FitComparison <- '056_048_St'

SolFits56_127St<-SolFitsExpFitAll %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_056" | Strain == "PE-rich_127")  
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits56_127St)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_56_127St<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_56_127St$FitComparison <- '056_127_St'

SolFits48_127St<-SolFitsExpFitAll %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PE-rich_048" | Strain == "PE-rich_127")  
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits48_127St)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_48_127St<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_48_127St$FitComparison <- '048_127_St'

SolFits77_48St<-SolFitsExpFitAll %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_077" | Strain == "PE-rich_048") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits77_48St)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_77_48St<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_77_48St$FitComparison <- '077_048_St'

SolFits77_127St<-SolFitsExpFitAll %>%
  filter(Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_077" | Strain == "PE-rich_127") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Strain + PARPhotonDose_day:Strain,data=SolFits77_127St)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_77_127St<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_77_127St$FitComparison <- '077_127_St'

modelSt<-rbind(model_56_77St, model_56_48St, model_56_127St, model_48_127St, model_77_48St, model_77_127St)
  rm(model_56_77St, model_56_48St, model_56_127St, model_48_127St, model_77_48St, model_77_127St)
```

t-test from the linear model Phase
```{r}
# Exp
Stats56_ExpSt<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential" | Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_056") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Phase + PARPhotonDose_day:Phase,data=Stats56_ExpSt)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_56ExpSt<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_56ExpSt$FitComparison <- '056_Exp_St'

Stats77_ExpSt<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential" | Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PC-rich_077") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Phase + PARPhotonDose_day:Phase,data=Stats77_ExpSt)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_77ExpSt<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_77ExpSt$FitComparison <- '077_Exp_St'

Stats48_ExpSt<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential" | Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PE-rich_048") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Phase + PARPhotonDose_day:Phase,data=Stats48_ExpSt)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_48ExpSt<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_48ExpSt$FitComparison <- '048_Exp_St'

Stats127_ExpSt<-SolFitsExpFitAll %>%
  filter(Phase == "Exponential" | Phase == "Pre-stationary") %>%
  filter(Ex_WL == 445) %>%
  filter(Strain == "PE-rich_127") 
  fit <- lm(Sig_nm2psii ~ PARPhotonDose_day + Phase + PARPhotonDose_day:Phase,data=Stats127_ExpSt)
x <- cbind(t(as.numeric(coefficients(fit))), t(as.numeric(summary(fit)$coefficients[4, 4])), t(as.numeric(summary(fit)$coefficients[4, 3])), t(as.numeric(summary(fit)$coefficients[4, 2])))
model_127ExpSt<-data.frame(unclass(x), check.names = FALSE, stringsAsFactors = FALSE) %>% 
  rename("Estimate" = "4", "Std.Error" = "7", "t_value" = "6", "p_value" = "5") %>% 
  select(c("Estimate", "Std.Error", "t_value", "p_value"))
  model_127ExpSt$FitComparison <- '127_Exp_St'


modelExpSt<-rbind(model_56ExpSt, model_77ExpSt, model_48ExpSt, model_127ExpSt)
  rm(model_56ExpSt, model_77ExpSt, model_48ExpSt, model_127ExpSt, x)
```

# Merge statistic
```{r}
Anova_Sig445_Model<-rbind(modelExp, modelSt, modelExpSt)
rm(modelExp, modelSt, modelExpSt)
```

# Save RDS that create stats and tables

```{r}
saveRDS(Anova_Sig445_Model, file.path(TableRdsPath, paste(Project, "Anova_Sig445_Model.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```


------------------------------------------------------# Add Turner Catalog--------------------------------------------------

# Load Turner catalog

```{r load turner catalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
Turnercatalog<- read_sheet("https://docs.google.com/spreadsheets/d/13mQm0B3siS65UuGjNdzvpHFomfuwn6aAg7dBoq1IqrM/edit#gid=0")

as.data.frame(Turnercatalog)
ChlData <- Turnercatalog 

ChlData <- ChlData %>%  
  mutate(TurChl_ugL = as.numeric(Reading_rfu) * as.numeric(Chl_slope) + as.numeric(Chl_intercept)) %>% 
  mutate(DATE = ymd(`DATE`)) %>% 
  rename(SampleID=CultureID) %>% 
  rename(ObsDate=DATE) %>% 
  select(c(SampleID, ObsDate, TurChl_ugL)) %>% 
  filter(TurChl_ugL<212354.754)  #outliers

```

```{r}
ChlData <- ChlData %>%  
  filter(TurChl_ugL<1500)
```


# Calculate Chl mean from 3 technical replica

```{r}
ChlData <- ChlData %>%
  group_by(SampleID, ObsDate) %>%
  summarize(SampleID, ObsDate, TurChl_ugL,
            meanTurChl_ugL = mean(TurChl_ugL),
            sdTurChl_ugL = sd(TurChl_ugL)) %>%
  ungroup()
```


# Merge Sigma with chlorophyll Turner data 
It is "bigger" df than SolFitsPigmentExp, b/c I have 3 replica for Turner

```{r}
SolFitsExpStTurner <- ChlData %>%
  full_join(., SolFitsExpSt, by = c("SampleID"="SampleID", "ObsDate"="ObsDate")) %>% 
  drop_na(Strain)
```

# Filter only revelant strains

```{r}
SolFitsExpStTurner<-SolFitsExpStTurner %>%   
  filter(Strain=="PC-rich_056" | Strain == "PC-rich_077" | Strain == "PE-rich_048" | Strain == "PE-rich_127")
```


# Create preliminary JVPSII vs Chl Turner (ug/L) plot

```{r preliminary plots, warning = FALSE}
SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = TurChl_ugL, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = AllmeanJVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()


SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_ETRqpOxbo_aLHII_Sig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()
```



# Clean the environment

```{r}
rm(tMaxAGLines_056, tMaxAGLines_077, tMaxAGLines_048, tMaxAGLines_127, tmaxAG, data_text_AnovaExp56P, data_text_AnovaExp77P, data_text_AnovaExp48P, data_text_AnovaExp127P, data_text_AnovaExp56, data_text_AnovaExp77, data_text_AnovaExp48, data_text_AnovaExp127, data_text_AnovaSt56P, data_text_AnovaSt77P, data_text_AnovaSt48P, data_text_AnovaSt127P, data_text_AnovaSt56, data_text_AnovaSt77, data_text_AnovaSt48, data_text_AnovaSt127, data_text_AnovaPhase, fit, fitted445, model, augmented445, SolFits48_127Exp, SolFits48_127Exp, SolFits56_127Exp, SolFits56_127St, SolFits56_48Exp, SolFits56_48St, SolFits77_48Exp, SolFits77_48St, SolFits77_127Exp, SolFits77_127St, SolFits48_127St, Stats56_77Exp, Stats56_77St, Stats56_ExpSt, Stats56_ExpSt, Stats77_ExpSt, Stats48_ExpSt, Stats127_ExpSt, SigFit445Stats, SolFitsExpFitAll445, SolFitsExpFit445Clean, SolFitsExpFitAll, SolFitsExpSt, ChlData, Turnercatalog)
```

# Save Rds for further analysis

```{r save rds}
saveRDS(SolFitsExpStTurner, file.path(DataOut, paste(Project, "Processed_SolisenseData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(SolFitsExpStTurner)
```






The anova() function will take the model objects as arguments, and return an ANOVA testing whether the more complex model is significantly better at capturing the data than the simpler model. If the resulting p-value is sufficiently low (usually less than 0.05), we conclude that the more complex model is significantly better than the simpler model, and thus favor the more complex model. If the p-value is not sufficiently low (usually greater than 0.05), we should favor the simpler model.

# Exstracting models for each fit - models were not all fitted to the same size of dataset

```{r}
# StatsSigLM<-SolFitsAllPigmentPCPE %>% 
#   drop_na(Sig_nm2psii, AllmeanPhycoChlaRatio) 
# 
# StatsSigLM$Strain <- factor(StatsSigLM$Strain)
# StatsSigLM$Phase <- factor(StatsSigLM$Phase)  
# StatsSigLM$AllmeanPhycoChlaRatio <- factor(StatsSigLM$AllmeanPhycoChlaRatio) 
# 
# SolFitsBA56Exp<-StatsSigLM %>%
#   filter(Strain == "PC-rich_056")
#   SolFitsBA56Exp <- SolFitsBA56Exp[-c(883:990), ]
# 
# SolFitsBA77Exp<-StatsSigLM %>%
#   filter(Strain == "PC-rich_077") 
#   SolFitsBA77Exp <- SolFitsBA77Exp[-c(883:998), ]
# 
# SolFitsBA48Exp<-StatsSigLM %>%
#   filter(Strain == "PE-rich_048") 
#   SolFitsBA48Exp <- SolFitsBA48Exp[-c(883:883), ]
# 
# SolFitsBA127Exp<-StatsSigLM %>%
#   filter(Strain == "PE-rich_127") 
#   SolFitsBA127Exp <- SolFitsBA127Exp[-c(883:894), ]
# 
# model1 <- lm(Sig_nm2psii~AllmeanPhycoChlaRatio, data = SolFitsBA56Exp)
# model2 <- lm(Sig_nm2psii~AllmeanPhycoChlaRatio, data = SolFitsBA77Exp)
# ANOVA_LinModel<-anova(model1, model2, test="F")
#   
#   
# model<-aov(Sig_nm2psii~AllmeanPhycoChlaRatio*Phase*Strain, data=StatsSigLM)
# AnovaTest_SigLM<-data.frame(unclass(summary(model)), check.names = FALSE, stringsAsFactors = FALSE)
# TukeyHSDTest_Sig<-TukeyHSD(model, which = c("Phase", "Strain"))


#  diamonds.mod1 <- lm(Sig_nm2psii~PhycoChlaRatio, data = SolFitsAllExp)
#   diamonds.mod2 <- lm(Sig_nm2psii~PhycoChlaRatio, data = SolFitsAllSt)
#   anova(diamonds.mod1, diamonds.mod2, test="Chisq")

```


```{r}
#108 value per 1 condition - b/c mean OD
# Test<-SolFitsAllPigmentPCPETurner %>% 
#   filter(Strain == "PC-rich_077") %>% 
#   filter(Photoperiod == 12) %>% 
#   filter(Par_ue == 90) %>% 
#   filter(Ex_WL == 445)
```


dodawanie modeli zeby sprawdzic, czy sa istotne roznice pomiedzy szczepami i fazami wzrostu
https://stats.stackexchange.com/questions/435644/is-there-a-method-to-look-for-significant-difference-between-two-linear-regressi

```{r}
# set.seed(123)
# df = data.frame(Age=sample(1:100))
# df$Height[1:50] = df$Age[1:50] + rpois(50,30)
# df$Height[51:100] = 1.3*df$Age[51:100] + rpois(50,30)
# df$Fladen = rep(c("A","B"),each=50)
# 
# summary(lm(Height ~ Age + Fladen + Age:Fladen,data=df))

# So the last term, Age:FladenB shows a coefficient of 0.29, meaning the slope (Height vs Age) in Fladen B is .29 more than that in Fladen A

# StatsExp590<-SolFitsAllPigmentPCPE %>%
#   filter(Phase == "Exponential") %>%
#   filter(Ex_WL == 590) %>%
#   select(c(Strain, Sig_nm2psii, AllmeanPhycoChlaRatio))
# summary(lm(Sig_nm2psii ~ AllmeanPhycoChlaRatio + Strain + AllmeanPhycoChlaRatio:Strain,data=StatsExp590))

```

# compact letter display
```{r}
# # analysis of variance
# anova <- aov(weight ~ feed, data = chickwts)
# 
# # Tukey's test
# tukey <- TukeyHSD(anova)
# 
# # compact letter display
# cld <- multcompLetters4(anova, tukey)
# 
# # table with factors and 3rd quantile
# dt <- group_by(chickwts, feed) %>%
#   summarise(w=mean(weight), sd = sd(weight)) %>%
#   arrange(desc(w))
# 
# # extracting the compact letter display and adding to the Tk table
# cld <- as.data.frame.list(cld$feed)
# dt$cld <- cld$Letters
# 
# print(dt)
```






Set up R codes for Greek letters

\u0391  Α   Greek Capital Letter Alpha
\u0392  Β   Greek Capital Letter Beta
\u0393  Γ   Greek Capital Letter Gamma
\u0394  Δ   Greek Capital Letter Delta
\u0395  Ε   Greek Capital Letter Epsilon
\u0396  Ζ   Greek Capital Letter Zeta
\u0397  Η   Greek Capital Letter Eta
\u0398  Θ   Greek Capital Letter Theta
\u0399  Ι   Greek Capital Letter Iota
\u039A  Κ   Greek Capital Letter Kappa
\u039B  Λ   Greek Capital Letter Lambda
\u039C  Μ   Greek Capital Letter Mu
\u039D  Ν   Greek Capital Letter Nu
\u039E  Ξ   Greek Capital Letter Xi
\u039F  Ο   Greek Capital Letter Omicron
\u03A0  Π   Greek Capital Letter Pi
\u03A1  Ρ   Greek Capital Letter Rho
\u03A3  Σ   Greek Capital Letter Sigma
\u03A4  Τ   Greek Capital Letter Tau
\u03A5  Υ   Greek Capital Letter Upsilon
\u03A6  Φ   Greek Capital Letter Phi
\u03A7  Χ   Greek Capital Letter Chi
\u03A8  Ψ   Greek Capital Letter Psi
\u03A9  Ω   Greek Capital Letter Omega
\u03B1  α   Greek Small Letter alpha
\u03B2  β   Greek Small Letter beta
\u03B3  γ   Greek Small Letter gamma
\u03B4  δ   Greek Small Letter delta
\u03B5  ε   Greek Small Letter epsilon
\u03B6  ζ   Greek Small Letter zeta
\u03B7  η   Greek Small Letter eta
\u03B8  θ   Greek Small Letter theta
\u03B9  ι   Greek Small Letter iota
\u03BA  κ   Greek Small Letter kappa
\u03BB  λ   Greek Small Letter lambda
\u03BC  μ   Greek Small Letter mu
\u03BD  ν   Greek Small Letter nu
\u03BE  ξ   Greek Small Letter xi
\u03BF  ο   Greek Small Letter omicron
\u03C0  π   Greek Small Letter pi
\u03C1  ρ   Greek Small Letter rho
\u03C2  ς   Greek Small Letter final sigma
\u03C3  σ   Greek Small Letter sigma
\u03C4  τ   Greek Small Letter tau
\u03C5  υ   Greek Small Letter upsilon
\u03C6  φ   Greek Small Letter phi
\u03C7  χ   Greek Small Letter chi
\u03C8  ψ   Greek Small Letter psi
\u03C9  ω   Greek Small Letter omega





