---
title: "Process_MCDielLight"
author:
- Douglas A. Campbell
- Sylwia Wilczewska-Wilinska
date: "`r format(Sys.Date())`"
bibliography: Prochlorococcus_O2_NPQ.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---
# This Rmd loads previously imported,  tidied data from the PSI MC and generates estimates of hourly and diel cumulative photon dose to cultures.

# Set Options

## Set figure caption font size

```{css, echo=FALSE}
p.caption {
  font-size: 18px;
}
```

## Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

```{r libraries}
library(tidyverse)
library(zoo)
library(e1071)
library(gcookbook)  # Load gcookbook for the uspopage data set
library(viridis)  # Load viridis for the viridis palette
library("RColorBrewer")
```

```{r colour setting}
# Bin4_nm <- c(440, 510, 590, 660)
# Bin4Colours <- c(w_length2rgb(440), w_length2rgb(510), w_length2rgb(590), w_length2rgb(660))
# names(Bin4Colours) <- Bin4_nm
```

```{r set project variables}
Project <- "BalticPhotoperiod"
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedMCDielLightData")
#DataIn <- file.path("..", "Data", "ImportedData", "ImportedMCData", fsep = .Platform$file.sep)

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")

FileEncode <- "UTF-8" 
Delimiter <- ""
HeaderRows <- 0
```

## Read Data
```{r read data}
MCFiles <- list.files(path = file.path("..", "Data", "ImportedData", "ImportedMCData"), full.names = TRUE)
MCFiles

MCData1 <- readRDS(file = MCFiles[1])


 MCDataAll <- map_df(MCFiles, readRDS)

  # ungroup() |>
  # mutate(deltaOD = OD680 - OD720)
  # colnames(MCData)
```


# Read MetaData Catalog

```{r read locally stored metadata from rds}
# MC_RUN39 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20211214_PICO_MC247_RUN39_TargetDataMetaFilter.Rds"))
# MC_RUN40 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20211223_PICO_MC257_RUN40_TargetDataMetaFilter.Rds"))
# MC_RUN43 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20211229_PICO_MC247_RUN43_TargetDataMetaFilter.Rds"))
# MC_RUN44 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220107_PICO_MC257_RUN44_TargetDataMetaFilter.Rds"))
# MC_RUN45 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220113_PICO_MC247_RUN45_TargetDataMetaFilter.Rds"))
# MC_RUN46 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220122_PICO_MC257_RUN46_TargetDataMetaFilter.Rds"))
# MC_RUN50 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220206_PICO_MC257_RUN50_TargetDataMetaFilter.Rds"))
# MC_RUN60 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220405_PICO_MC247_RUN60_TargetDataMetaFilter.Rds"))
# MC_RUN62 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220410_PICO_MC257_RUN62_TargetDataMetaFilter.Rds"))
# MC_RUN65 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220420_PICO_MC257_RUN65_TargetDataMetaFilter.Rds"))
# MC_RUN71 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220507_PICO_MC257_RUN71_TargetDataMetaFilter.Rds"))
# MC_RUN74 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220607_PICO_MC257_RUN74_TargetDataMetaFilter.Rds"))
# MC_RUN77 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20220615_PICO_MC257_RUN77_TargetDataMetaFilter.Rds"))
# MC_RUN121 <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMCData", "20230816_PICO_MC257_RUN121_TargetDataMetaFilter.Rds"))
```

```{r}
# MCData_8<- rbind(MC_RUN43, MC_RUN46, MC_RUN65)
# MCData_8<-MCData_8 %>% 
#     mutate(deltaOD = OD680 - OD720)
# 
# MCData_12<- rbind(MC_RUN39, MC_RUN44, MC_RUN62)
# MCData_12<-MCData_12 %>% 
#     mutate(deltaOD = OD680 - OD720)
# 
# MCData_16<- rbind(MC_RUN40, MC_RUN45, MC_RUN50, MC_RUN60)
# MCData_16<-MCData_16 %>% 
#      mutate(deltaOD = OD680 - OD720)
# 
# MCData_24<- rbind(MC_RUN71, MC_RUN74, MC_RUN77, MC_RUN121)
# MCData_24<- MCData_24 %>% 
#      mutate(deltaOD = OD680 - OD720)
# 
# rm(MC_RUN43, MC_RUN46, MC_RUN65, MC_RUN39, MC_RUN44, MC_RUN62, MC_RUN40, MC_RUN45, MC_RUN50, MC_RUN60, MC_RUN71, MC_RUN74, MC_RUN77, MC_RUN121)
```

```{r par_time_plot}

MCDataAll |>
ggplot() +
  geom_point(aes(x = time, y = Actinic_par, colour = WL)) +
  facet_grid(cols = vars(Tube), rows = vars(Filename)) +
  theme_bw()

MCDataAll |>
ggplot() +
  geom_point(aes(x = time, y = Actinic_par, colour = WL)) +
  facet_grid(cols = vars(Strain), rows = vars(Photoperiod, Par_ue)) +
  theme_bw()

# MCData_12 |>
#   filter(Run == 39) %>% 
#   ggplot() +
#   geom_point(aes(x = time, y = Actinic_par, colour = WL)) +
#   facet_grid(cols = vars(Tube)) +
#   theme_bw()
# 
# MCData_12 |>
#   filter(Run == 39) %>% 
#   filter(time >= 48,
#          time <= 72) |>
#   ggplot() +
#   geom_point(aes(x = time, y = Actinic_par, colour = WL)) +
#   facet_grid(cols = vars(Tube)) +
#   theme_bw()
# 
# MCData_12 |>
#   filter(Run == 39) %>% 
#   filter(time >= 48,
#          time <= 72) |>
#   ggplot() +
#   geom_point(aes(x = time, y = deltaOD, colour = WL)) +
#   facet_grid(cols = vars(Tube)) +
#   theme_bw()
# 
# MCData_12 |>
#   filter(Run == 39) %>% 
#   filter(time >= 48,
#          time <= 72) |>
#   ggplot() +
#   geom_point(aes(x = time, y = Actinic_par)) +
#   geom_point(aes(x = time, y = 1000 * deltaOD, colour = WL)) +
#   facet_grid(cols = vars(Tube)) +
#   theme_bw()
# 
# 
# MCData_12 |>
#   filter(Run == 39) %>% 
#   filter(Tube == 2) |>
#   # filter(time >= 48,
#   #        time <= 72) |>
#   ggplot() +
#   geom_point(aes(x = time, y = Actinic_par)) +
#   geom_point(aes(x = time, y = 1000 * deltaOD, colour = WL)) +
#   facet_grid(cols = vars(Photoperiod, Tube)) +
#   theme_bw()
```

#https://stackoverflow.com/questions/76603287/calculate-linear-regression-slope-with-moving-window
```{r growth rates}

# slope <- function(x) coef(lm(x[, 2] ~ x[, 1]))[[2]]
slope <- function(x) cov(x[, 1], x[, 2]) / var(x[, 1])

#FitWindow_h <- 2
#maybe issues still with changes in light level that do not align with growth measurement points

#maybe should estimate growth rates, then use 'summarize' to do sum of actinic photon dose for each hour?

MCDataHour_8 <- MCData_8 |>
  group_by(Filename, Tube, Day, Run) |>
  filter(deltaOD >= 0) |>
  mutate(Actinic_photonsm2h = zoo::rollsum(Actinic_par, k = 8, fill = NA, align = "right") * 5 * 60) |> 
  mutate(mu_deltaODwindow = rollapply(cbind(time, log(deltaOD)), 24, slope, by.column=FALSE, fill=NA)) |>
  #mutate(mu_Averh = zoo::rollmean(mu_deltaODwindow, k = 12, fill = NA, align = "right")) |>
  ungroup() |>
  filter(time - round(time) == 0)

MCDataHour_12 <- MCData_12 |>
  group_by(Filename, Tube, Day, Run) |>
  filter(deltaOD >= 0) |>
  mutate(Actinic_photonsm2h = zoo::rollsum(Actinic_par, k = 12, fill = NA, align = "right") * 5 * 60) |> 
  mutate(mu_deltaODwindow = rollapply(cbind(time, log(deltaOD)), 24, slope, by.column=FALSE, fill=NA)) |>
  #mutate(mu_Averh = zoo::rollmean(mu_deltaODwindow, k = 12, fill = NA, align = "right")) |>
  ungroup() |>
  filter(time - round(time) == 0)

MCDataHour_16 <- MCData_16 |>
  group_by(Filename, Tube, Day, Run) |>
  filter(deltaOD >= 0) |>
  mutate(Actinic_photonsm2h = zoo::rollsum(Actinic_par, k = 16, fill = NA, align = "right") * 5 * 60) |> 
  mutate(mu_deltaODwindow = rollapply(cbind(time, log(deltaOD)), 24, slope, by.column=FALSE, fill=NA)) |>
  #mutate(mu_Averh = zoo::rollmean(mu_deltaODwindow, k = 12, fill = NA, align = "right")) |>
  ungroup() |>
  filter(time - round(time) == 0)

MCDataHour_24 <- MCData_24 |>
  group_by(Filename, Tube, Day, Run) |>
  filter(deltaOD >= 0) |>
  mutate(Actinic_photonsm2h = zoo::rollsum(Actinic_par, k = 24, fill = NA, align = "right") * 5 * 60) |> 
  mutate(mu_deltaODwindow = rollapply(cbind(time, log(deltaOD)), 24, slope, by.column=FALSE, fill=NA)) |>
  #mutate(mu_Averh = zoo::rollmean(mu_deltaODwindow, k = 12, fill = NA, align = "right")) |>
  ungroup() |>
  filter(time - round(time) == 0)
```

# Merge All MC data

```{r}
MCDataHour<-rbind(MCDataHour_8, MCDataHour_12, MCDataHour_16, MCDataHour_24)
```


# Create preliminary plot

```{r}
MCDataHour |>
    filter(Run == 39) %>% 
  # filter(time >= 48,
  #        time <= 72) |>
  filter(time < 100) |>
  ggplot() +
  geom_point(aes(x = time, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  geom_point(aes(x = time, y = deltaOD), colour = "green") +
  #geom_point(aes(x = time, y = mu_Averh)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour |>
    filter(Run == 39) %>% 
  filter(Tube == 5) %>%
  filter(time >= 48,
         time <= 72) |>
  #filter(time < 24) |>
  ggplot() +
  geom_point(aes(x = time, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  geom_point(aes(x = time, y = deltaOD), colour = "green") +
  #geom_point(aes(x = time, y = mu_Averh)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()
```


```{r hourly plots exploration}
#temporary
#use case_when to remove 'dark' periods?
#bad to filter and only then estimate growth rates; better to do across 1 h window

MCDataHour |>
  filter(Run == 39) %>% 
   filter(time <= 100) |>
  ggplot() +
  geom_point(aes(x = time, y = Actinic_photonsm2h, colour = WL)) +
  geom_point(aes(x = time, y = mu_deltaODwindow * 10000)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour |>
  filter(Run == 39) %>% 
   filter(time <= 100) |>
  ggplot() +
  geom_point(aes(x = Actinic_photonsm2h, y = mu_deltaODwindow, colour = ToD)) +
  geom_line(aes(x = Actinic_photonsm2h, y = mu_deltaODwindow, colour = ToD)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour |>
    filter(Run == 39) %>% 
   filter(time <= 100) |>
  ggplot() +
  geom_point(aes(x = ToD, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  geom_line(aes(x = ToD, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour |>
    filter(Run == 39) %>% 
  filter(Tube == 2) |>
  ggplot() +
  geom_point(aes(x = ToD, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  geom_line(aes(x = ToD, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

MCDataHour |>
    filter(Run == 39) %>% 
   filter(time <= 100) |>
  #filter(Actinic_par > 1) |>
  ggplot() +
  geom_point(aes(x = ToD, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  geom_line(aes(x = ToD, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  geom_smooth(aes(x = ToD, y = mu_deltaODwindow)) +
  facet_grid(cols = vars(Tube)) +
  theme_bw()


myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(100, 1000000))
MCDataHour |>
  filter(Run == 39) %>% 
  filter(Tube == 5) %>%
  filter(time <= 250) |>
  filter(time >= 48) |>
  #filter(Actinic_par > 1) |>
  ggplot() +
  geom_point(aes(x = time, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  geom_line(aes(x = time, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
  sc +
  facet_grid(cols = vars(Tube)) +
  theme_bw()

```


------------------------------# Support Vector regression---------------------------------------------------

https://www.geeksforgeeks.org/support-vector-regression-svr-using-linear-and-non-linear-kernels-in-scikit-learn/

https://minimatech.org/non-linear-regression-with-r/

# Support Vector regression

```{r}
MCDataHourTest <- MCDataHour %>%
  select(c(time, ToD, Day, mu_deltaODwindow, Actinic_photonsm2h, SampleID, Strain, Tube, Run, Par_ue, Photoperiod, OD720, OD680, deltaOD, Actinic_par, WL, O2)) %>%
  drop_na(mu_deltaODwindow) %>% 
  drop_na(Actinic_photonsm2h) 

# Function to train an SVM model and make predictions
train_and_predict_svm <- function(data) {
  svr_model <- svm(mu_deltaODwindow ~ time, data = data, kernel = 'radial',
                   cost = 24, gamma = 100)
  data$svr_pred <- predict(svr_model, data)
  return(data)
}

# Group by Tube, train SVM model, and make predictions within each group
result <- MCDataHourTest %>%
  group_by(Tube, Run) %>%
  nest() %>%
  mutate(data = map(data, train_and_predict_svm)) %>%
  unnest(data) %>%
  ungroup()

# Calculate the root mean squared error for each group
RMSE_by_Tube <- result %>%
  group_by(Tube, Run) %>%
  summarise(RMSE = sqrt(mean((mu_deltaODwindow - svr_pred)^2)))

```

# Rename all imported data into one df containing predictions (svr_pred)

```{r}
MCImportAll<-result
```

# Clean the environment

```{r}
rm(MCData_8, MCData_12, MCData_16, MCData_24, MCDataHour_8, MCDataHour_12, MCDataHour_16, MCDataHour_24, result, MCDataHourTest, myPalette, sc)
```

# Save Rds for further analysis

```{r save rds}
saveRDS(MCImportAll, file.path(DataOut, paste(Project, "Processed_MCDielLightData2.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
colnames(MCImportAll)
```

# Create preliminary plot

```{r}
# Plot the results
MCImportAll %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 16) %>% 
  ggplot() +
  geom_point(aes(x = time, y = mu_deltaODwindow), alpha = 0.4) +
  geom_line(aes(x = time, y = svr_pred, color = 'SVR_radial'), size = 1.3) +
  geom_line(aes(x = time, y = mu_deltaODwindow)) +
    geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 2 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 3 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 4 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 5 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 6 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 8 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 9 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 10 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 11 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 12 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 13 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
  theme_bw()

MCImportAll %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "BA127R") %>% 
  ggplot() +
  geom_point(aes(x = time, y = mu_deltaODwindow), alpha = 0.4) +
  geom_line(aes(x = time, y = svr_pred, color = 'SVR_radial'), size = 1.3) +
  geom_line(aes(x = time, y = mu_deltaODwindow)) +
    geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 2 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 3 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 4 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 5 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 6 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 8 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 9 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 10 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 11 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 12 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 13 * 24), linetype = "dashed") + 
    geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
  theme_bw()
```


# Add facets labels and change strain name to create plot

```{r add facets labels and change strain names}
MCImportAll$facetsPar_ue = factor(MCImportAll$O2, labels = c("PAR~(µmol~photons~m^{-2}~s^{-1})"))
MCImportAll$facetsPhotoperiod = factor(MCImportAll$WL, labels = c("Photoperiod~(h)"))

MCImportAll <- MCImportAll %>% 
  filter(Strain == "BA127R" | Strain == "BA48R" | Strain == "BA56G" | Strain == "BA77G") %>% 
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 
```

# Create preliminary plot

```{r fig.height = 8, fig.width = 8, warning = FALSE}
#https://jmsallan.netlify.app/blog/the-brewer-palettes/
myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
sc <- scale_colour_gradientn(colours = myPalette(10))

MCImportAll %>%
  filter(Par_ue == 300) %>% 
  filter(Photoperiod == 12) %>% 
  filter(Strain == "PE-rich_048" | Strain == "PC-rich_077") %>% 
  ggplot() +
  #geom_point(aes(x = time, y = mu_deltaODwindow), alpha = 0.4) +
  geom_point(aes(x = time, y = mu_deltaODwindow, colour = Actinic_photonsm2h), alpha = 0.9) +
  geom_line(aes(x = time, y = svr_pred), color = 'blue', size = 0.7) +
  #geom_line(aes(x = time, y = mu_deltaODwindow)) +
  sc +
  #scale_colour_discrete() + 
    geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 10 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 11 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 12 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 13 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 14 * 24), linetype = "dotted", alpha = 0.4) + 
  facet_grid(rows = vars(Strain), cols = vars (Photoperiod)) +
  theme_bw()
```


# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_HourlyGrowthRateExample333",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```


# Create GrowthCurve plot

```{r create GrowthCurve plot, fig.height = 8, fig.width = 8, warning = FALSE}
MCImportAll %>%
  filter(time <200) %>% 
 #filter(time >48) %>% 
  #filter(Par_ue != 600) %>% 
  filter(Run != 77) %>% 
  ggplot() +
  geom_point(aes(x = time, y = mu_deltaODwindow, colour = as.factor(Strain)), alpha = 0.2) +
  geom_line(aes(x = time, y = svr_pred, colour = as.factor(Strain)), size = 0.6) +
    geom_vline(aes(xintercept = 1 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 2 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 3 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 4 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 5 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 6 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 7 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 8 * 24), linetype = "dotted", alpha = 0.4) + 
    geom_vline(aes(xintercept = 9 * 24), linetype = "dotted", alpha = 0.4) + 
    # geom_vline(aes(xintercept = 10 * 24), linetype = "dashed") + 
    # geom_vline(aes(xintercept = 11 * 24), linetype = "dashed") + 
    # geom_vline(aes(xintercept = 12 * 24), linetype = "dashed") + 
    # geom_vline(aes(xintercept = 13 * 24), linetype = "dashed") + 
    # geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="") +
  scale_y_continuous(breaks=seq(-0.5, 0.5, by = 0.25)) +
  coord_cartesian(ylim = c(-0.5, 0.5)) +
  #labs(y = "Optical density ("~OD[680]~")", x = "Elapsed time (h)") +
  ggh4x::facet_nested(cols = vars(facetsPhotoperiod, Photoperiod), rows = vars(facetsPar_ue, Par_ue), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.96),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=11))
```

# Save plot 

```{r save plot}
ggsave(file = file.path(FigPath, paste("SFig_HourlyGrowthRate",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Support Vector regression

```{r}
# library(e1071)
# svr_model <- svm(mu_deltaODwindow ~ time, data = MCDataHourTest, kernel = 'radial',
#                  cost = 24, gamma = 100)
# resid_svr <- MCDataHourTest$mu_deltaODwindow - predict(svr_model)
# sqrt(mean(resid_svr ^ 2))
```

```{r}
# ## test residuals
# test_resid_svr <- MCDataHourTest$mu_deltaODwindow - predict(svr_model, MCDataHourTest)
# ## test RMSE
# sqrt(mean(test_resid_svr ^ 2))
# ## R Squared
# cor(MCDataHourTest$mu_deltaODwindow, predict(svr_model, MCDataHourTest)) ^ 2
# 
# MCDataHourTest$svr_pred <- predict(svr_model, MCDataHourTest)
```

```{r}
# MCDataHourTest <-MCDataHour %>% 
#   select(c(time, Day, mu_deltaODwindow, Actinic_photonsm2h, Tube)) %>% 
#   filter(Tube == 5) %>% 
#   #filter(time >= 24) %>% 
#    # filter(time <= 240) %>% 
#   drop_na(mu_deltaODwindow)
#   
# myPalette <- colorRampPalette(rev(brewer.pal(11, "Spectral")))
# sc <- scale_colour_gradientn(colours = myPalette(100), limits=c(100, 1000000))
# 
# MCDataHourTest |>
#   ggplot() +
#   geom_point(aes(x = time, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
#   geom_line(aes(x = time, y = mu_deltaODwindow, colour = Actinic_photonsm2h)) +
#   sc +
#     geom_vline(aes(xintercept = 1 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 2 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 3 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 4 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 5 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 6 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 7 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 8 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 9 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 10 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 11 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 12 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 13 * 24), linetype = "dashed") + 
#     geom_vline(aes(xintercept = 14 * 24), linetype = "dashed") + 
#   facet_grid(cols = vars(Tube)) +
#   theme_bw()
```



