---
title: "Process_SolisenseLRCData"
author:
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Process_SolisenseDataLRC.Rmd process BalticPhotoperiod_Imported_SolisenseLight_LRC.Rds from BalticPhotoperiod/Data/ImportedData/ImportedSolisenseData folder and stored in Data/ProcessedData/ProcessedSolisenseData folder as: BalticPhotoperiod_Processed_Solisense_LRC.Rds

# Load Libraries

```{r load libraries, warning = FALSE, echo=FALSE} 
library(ggtext)
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(ggpubr)
library(googledrive)
library(googlesheets4)
library(readxl)
library(Cairo) #for greek symbols
library(data.table)
library(purrr)
library(minpack.lm) #Standard 'nls' framework that uses 'nls.lm' for fitting
```



# Set Project Variables 

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
Project <- "BalticPhotoperiod"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedSolisenseData")
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisenseData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
# FileID <- "fit"
# FileEncode <- "UTF-8"
# Delimiter <- ","
# HeaderRows <- 0
```

# Read Imported Solisense

```{r read locally stored metadata from rds}
SolFitsMetaRaw <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedSolisenseData", "BalticPhotoperiod_Imported_SolisenseLight_LRC.Rds"))

SolFitsMetaRaw<-SolFitsMetaRaw
```

# Create preliminary plots 

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsMetaRaw %>%
  ggplot() +
  geom_point(aes(x = Par_ue, y = Sig, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  facet_grid(rows = vars(Ex_WL), cols = vars(Photoperiod)) +
  theme_bw()

```
# Change variable names for consistency

```{r}
SolFitsMetaRaw <- SolFitsMetaRaw %>%
  rename(FilenameSolisense=Filename)
```

# Create smaller value to for Platt model

```{r}
SolFitsMeta<-SolFitsMetaRaw %>%
  mutate(JVPSII_aLHIIOxbomax = JVPSII_aLHIIOxbomax/1e22) %>%
  mutate(JVPSII_ETRtauav_FoSig = JVPSII_ETRtauav_FoSig/1e22) %>%
  mutate(JVPSII_ETRqpOxbo_FoSig = JVPSII_ETRqpOxbo_FoSig/1e22) %>%
  mutate(JVPSII_ETRtauav_aLHII_Sig = JVPSII_ETRtauav_aLHII_Sig/1e22) %>%
  mutate(JVPSII_ETRqpOxbo_aLHII_Sig = JVPSII_ETRqpOxbo_aLHII_Sig/1e22)
```


# Create preliminary plots 

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsMeta %>%
  ggplot() +
  geom_point(aes(x = ActPARCorr, y = JVPSII_ETRqpOxbo_FoSig, colour = as.factor(Strain)), size = 3.5, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  facet_grid(cols = vars(Ex_WL, Photoperiod), rows = vars(Par_ue)) +
  theme_bw()

```


# Fit LRC for JVPSII to allow selection of specific JVPSII for different growth light levels.

```{r}
grcplatt <- function(I, a, b, Pmax){Pmax * (1-exp(-a*I/Pmax)) * exp(-b*I/Pmax)}

#`%notin%` <- negate(`%in%`)
# "ObsDate", "ObsTime","ObsDateTime","E_days", "Time_h", "StartDateTimeSol", "Time_mSec"
# filter(SampleID %notin% c("SySl1266") | ObsDate %notin% c("2022-06-14") | Ex_WL %notin% c(445)) %>%

SolFitsMetaLRC <- SolFitsMeta %>%
  nest(data = -c("SampleID", "Run", "Strain" ,"ExpDate","Par_ue", "Photoperiod", "O2", "WL", "MC", "Tube","Ex_WL","LightShape", "ExpEndDate", "PARPhotonDose_day", "ObsDate", "E_days")) %>% #head(50) %>% 
  mutate(GRCplatt_Model = map(data, possibly(~nlsLM(JVPSII_ETRqpOxbo_FoSig ~ grcplatt(I = ActPARCorr, a, b, Pmax),
         data = .x,
         control = list(maxiter = 100),
         start = list(a = 0.1/30, b = 0.01/800, Pmax = 6),lower = c(0, 0, 0))))) %>%
  mutate(GRCplatt_Param = map(GRCplatt_Model, tidy),
         GRCplatt_Predict = map(GRCplatt_Model, possibly(augment)),
         GRCplatt_Glance = map(GRCplatt_Model, possibly(glance)))


# GRCplatt_PredictSolFits <- SolFitsMetaLRC %>%
#   unnest(GRCplatt_Predict)%>%
#   unnest(GRCplatt_Param)
#   
```

# Create preliminary plot - Example

```{r prelim plot}
SolFitsMetaLRC |> 
  unnest(GRCplatt_Predict) |>
  filter(Strain == "BA48R") %>% 
  filter(Par_ue == 90) %>% 
  filter(Photoperiod == 16) |>
ggplot() +
  geom_point(aes(ActPARCorr, JVPSII_ETRqpOxbo_FoSig, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), alpha = 0.8, size = 3.5, show.legend = T) +
  geom_line(aes(ActPARCorr, .fitted), colour = "black", linetype = "dotted") +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain, Par_ue, Photoperiod, E_days), labeller = label_parsed) +
  theme_bw()

```

Use Peak Par_ue and 1/2 Peak Par_ue to estimate growth JVPSII for each combination
-use 'Pluck' to reach into GRCplatt_Predict to get a, b, Pmax; or
-unnest, pivot wider to get a, b, Pmax

```{r growth light JVPSII}

SolFitsMetaLRCGrowth <- SolFitsMetaLRC |>
  unnest(GRCplatt_Param) |>
  select(-c(statistic, p.value, GRCplatt_Predict, GRCplatt_Glance)) |> #remove (temporarily) to make pivot_wider easier
  pivot_wider(names_from = term, values_from = c(estimate, std.error)) |>
  mutate(JVPSII_Par_ue = grcplatt(I = Par_ue, a = estimate_a, estimate_b, estimate_Pmax),
         JVPSII_HalfPar_ue = grcplatt(I = (0.5*Par_ue), a = estimate_a, estimate_b, estimate_Pmax))

 
head(SolFitsMetaLRCGrowth) 
```

# Test plots of Growth Par_ue and 1/2 Growth Par_ue estimates for JVPSII
```{r growth JVPSII}
SolFitsMetaLRCGrowth |>
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = Ex_WL)) +
  facet_grid(cols = vars(Ex_WL, Photoperiod, Strain), rows = vars(Par_ue)) +
  theme_bw()

SolFitsMetaLRCGrowth |>
  filter(Strain == "BA48R") |>
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = Ex_WL)) +
  facet_grid(cols = vars(Ex_WL, Photoperiod, Strain), rows = vars(Par_ue)) +
  theme_bw()

SolFitsMetaLRCGrowth |>
  filter(Strain == "BA77G") |>
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = Ex_WL)) +
  facet_grid(cols = vars(Ex_WL, Photoperiod, Strain), rows = vars(Par_ue)) +
  theme_bw()
```
# Variable names used in Data Dictionary

```{r}
colnames(SolFitsMeta)
```


# Save Rds for further analysis

```{r save rds}
saveRDS(SolFitsMetaLRCGrowth, file.path(DataOut, paste(Project, "Processed_Solisense_LRC.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```



------------------------------------------------------# Add Turner Catalog--------------------------------------------------

# Load Turner catalog

```{r load turner catalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
Turnercatalog<- read_sheet("https://docs.google.com/spreadsheets/d/13mQm0B3siS65UuGjNdzvpHFomfuwn6aAg7dBoq1IqrM/edit#gid=0")

as.data.frame(Turnercatalog)
ChlData <- Turnercatalog 

ChlData <- ChlData %>%  
  mutate(TurChl_ugL = as.numeric(Reading_rfu) * as.numeric(Chl_slope) + as.numeric(Chl_intercept)) %>% 
  mutate(DATE = ymd(`DATE`)) %>% 
  rename(SampleID=CultureID) %>% 
  rename(ObsDate=DATE) %>% 
  select(c(SampleID, ObsDate, TurChl_ugL)) %>% 
  filter(TurChl_ugL<212354.754)  #outliers

```

# Calculate Chl mean from 3 technical replica

```{r}
ChlData <- ChlData %>%
  group_by(SampleID, ObsDate) %>%
  summarize(SampleID, ObsDate, TurChl_ugL,
            meanTurChl_ugL = mean(TurChl_ugL),
            sdTurChl_ugL = sd(TurChl_ugL)) %>%
  ungroup()
```


# Merge JVPSII with chlorophyll Turner data 
It is "bigger" df b/c I have 3 replica for Turner

```{r}
SolFitsExpStTurner <- ChlData %>%
  full_join(., SolFitsMetaLRCGrowth, by = c("SampleID"="SampleID", "ObsDate"="ObsDate")) %>% 
  drop_na(Strain)
```
```{r}
SolFitsExpStTurner<-SolFitsExpStTurner %>%  
  mutate(Strain=case_when(Strain=="BA127R"~"PE-rich_127",
         Strain=="BA48R"~"PE-rich_048",
        Strain=="BA56G"~"PC-rich_056",
         Strain=="BA77G"~"PC-rich_077")) 
```

# Filter only revelant strains

```{r}
SolFitsExpStTurner<-SolFitsExpStTurner %>%  
  filter(Strain=="PC-rich_056" | Strain == "PC-rich_077" | Strain == "PE-rich_048" | Strain == "PE-rich_127")
```


# Create preliminary JVPSII vs Chl Turner (ug/L) plot

```{r preliminary plots, warning = FALSE}
# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab1=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab2=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("600 µE"), expression("900 µE"))

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = JVPSII_Par_ue, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()

SolFitsExpStTurner %>% 
  ggplot() +
  geom_point(aes(x = meanTurChl_ugL, y = JVPSII_HalfPar_ue, colour = as.factor(Par_ue), shape = as.factor(Photoperiod)), size = 3.5, show.legend = T) +
  scale_shape_manual(values = c(15, 16, 17,18), name="", labels = lab1) +
  scale_colour_manual(values = c("darkslategray", "lightblue4", "hotpink4", "indianred3","goldenrod2", "khaki2"), name="", labels = lab2) +
  ggh4x::facet_nested(cols = vars(Ex_WL), rows = vars(Strain), labeller = label_parsed) +
  theme_bw()


```

--------------------------------- Adding cell_L ------------------------------

```{r set project variables}
Project <- "BalticPhotoperiod"
DataIn <- file.path("..", "Data", "ProcessedData", "ProcessedPigmentsData", fsep = .Platform$file.sep)
```

```{r Exported Rmd}
list.files(path = DataIn, pattern = Project, full.names = TRUE)
```

```{r read pigments File}
#df ontained mean OD per day from Multiculti and Abs from Olis spectra for selected nm. Based on this I calculated pigments per mL and per cell (pg/cell)

MCPigmentAllFile <- "../Data/ProcessedData/ProcessedPigmentsData/BalticPhotoperiod_Processed_PigmentsAll.Rds"
MCPigmentAllFileName <- str_split(string = MCPigmentAllFile, "/")[[1]][3] %>%
  str_remove(pattern = ".Rds")
MCPigmentAll <- readRDS(MCPigmentAllFile)  %>%
  ungroup()
```

```{r}
# colnames(MCPigmentAll)

MCPigmentAll<-MCPigmentAll %>% 
  select(-c(Phase, ChlaugmL, CarugmL, PEugmL, PCugmL, APCugmL, PhycougmL, CarChlaRatio, PhycoChlaRatio, PEPCRatio, Chlapgcell, Carpgcell, PEpgcell, PCpgcell, APCpgcell, Phycopgcell, meanOD720_h, meanDeltaOD_h, AchivePreStationary, dayRound_tmaxAG, MaxAG, MaxDG, MC))

```

```{r}
# MCPigmentAll <- MCPigmentAll %>%
#   filter(ToD==12) # When I choose 12 (peak) then I loose a few data point from 12h and 900UE
```

```{r}
SolFitsAll <- MCPigmentAll %>%
  full_join(., SolFitsExpStTurner, by = c("SampleID"="SampleID", "Strain"="Strain", "Run"="Run", "Tube"="Tube", "Par_ue" = "Par_ue", "Photoperiod"="Photoperiod", "O2"="O2", "WL"="WL", "LightShape"="LightShape", "ExpDate"="ExpDate", "ExpEndDate"="ExpEndDate", "PARPhotonDose_day"="PARPhotonDose_day","E_days"="E_days"))
```

```{r}
SolFitsAll<-SolFitsAll %>% 
  drop_na(JVPSII_Par_ue)
```

# Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAll %>%
  filter(Ex_WL == 445) %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsAll %>%
  filter(Ex_WL == 445) %>% 
  ggplot() +
  geom_point(aes(x = TurChl_ugL, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsAll %>%
  filter(Ex_WL == 445) %>% 
  ggplot() +
  geom_point(aes(x = cellL_OD680, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
```


# Choose only exp data

```{r choose only exp data}
O1 <- SolFitsAll %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 600 | Par_ue == 900) %>%
  filter(Photoperiod == 24) %>%
  filter(E_days <= 4)

O2 <- SolFitsAll %>%
  filter(Par_ue == 90 | Par_ue == 180 | Par_ue == 300) %>%
  filter(Photoperiod == 16) 
  #filter(E_days < 9)

O3 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 16) %>%
  filter(E_days <= 4)

O4 <- SolFitsAll %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 16) 
  #filter(E_days <= 14)

O5 <- SolFitsAll %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 8 | Photoperiod == 12) 
  #filter(E_days <=14)

O6 <- SolFitsAll %>%
  filter(Par_ue == 90) %>%
  filter(Photoperiod == 8) 
  #filter(E_days <=14)

O7 <- SolFitsAll %>%
  filter(Par_ue == 90) %>%
  filter(Photoperiod == 12) %>%
  filter(E_days <=10)

O8 <- SolFitsAll %>%
  filter(Par_ue == 180 | Par_ue == 300) %>%
  filter(Photoperiod == 8 | Photoperiod == 12) 
  #filter(E_days <=10)

O9 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 8 | Photoperiod == 12) %>%
  filter(E_days <=7)

O10 <- SolFitsAll %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 24) %>%
  filter(E_days <= 8)

SolFitsAllExp <-rbind(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)

rm(O1, O2, O3, O4, O5, O6, O7, O8, O9, O10)
```

# Choose only Stationary data 

```{r choose only St data}
O1 <- SolFitsAll %>%
  filter(Par_ue == 300 | Par_ue == 90 | Par_ue == 180 | Par_ue == 600 | Par_ue == 900) %>%
  filter(Photoperiod == 24) %>%
  filter(E_days > 4)

O2 <- SolFitsAll %>%
  filter(Par_ue == 30) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >14)

O3 <- SolFitsAll %>%
  filter(Par_ue == 90) %>%
  filter(Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O4 <- SolFitsAll %>%
  filter(Par_ue == 180 | Par_ue == 300) %>%
  filter(Photoperiod == 8 | Photoperiod == 12 | Photoperiod == 16) %>%
  filter(E_days >10)

O5 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 16) %>%
  filter(E_days >=6)

O6 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 12) %>%
  filter(E_days >=4)

O6 <- SolFitsAll %>%
  filter(Par_ue == 900 | Par_ue == 600) %>%
  filter(Photoperiod == 8) %>%
  filter(E_days >7)

SolFitsAllSt <-rbind(O1, O2, O3, O4, O5, O6)

rm(O1, O2, O3, O4, O5, O6)
```

# Combine Exp and St data

```{r}
  SolFitsAllExp$Phase <- 'Exponential'
  SolFitsAllSt$Phase <- 'Pre-stationary'

  SolFitsAllExpSt <-rbind(SolFitsAllExp, SolFitsAllSt)
  rm(SolFitsAllExp, SolFitsAllSt)
```


# Create preliminary plot

```{r preliminary plot}
lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))

SolFitsAllExpSt %>%
  filter(Ex_WL == 445) %>% 
  filter(Phase == "Exponential") %>% 
  ggplot() +
  geom_point(aes(x = E_days, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Phase, Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsAllExpSt %>%
  filter(Ex_WL == 445) %>% 
  filter(Phase == "Exponential") %>% 
  #filter(Photoperiod == 8) %>% 
  ggplot() +
  geom_point(aes(x = TurChl_ugL, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Phase, Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 

SolFitsAllExpSt %>%
  filter(Ex_WL == 445) %>% 
  filter(Phase == "Exponential") %>% 
  ggplot() +
  geom_point(aes(x = cellL_OD680, y = JVPSII_Par_ue, colour = as.factor(Strain)),  alpha = 0.8, size = 3, show.legend = T) +
  scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  ggh4x::facet_nested(cols = vars(Phase, Photoperiod), rows = vars(Par_ue), labeller = label_parsed) +
  theme_bw() 
```
# Save rds for further analysis

```{r save rds}
saveRDS(SolFitsAllExpSt, file.path(DataOut, paste(Project, "Processed_SolisenseJVPSII.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)

```

# Cleaning the environment

```{r}
rm(MCPigmentAll, ChlData, SolFitsExpStTurner, Turnercatalog)
```




-------------------------------------------- LIFT example plot ----------------------------------

# Set Project Variables 

```{r set project variables, read zipped files, list available files, warning = FALSE, echo=FALSE}
Project <- "BalticPhotoperiod"
DataIn <- file.path("..", "Data", "RawData", "SolisenseCurveData")
DataOut <- file.path("..", "Data", "ProcessedData", "ProcessedSolisenseData")

FigPath <- file.path("..", "Output", "Figures")
FigRdsPath <- file.path("..", "Output", "FiguresRds")
TableRdsPath <- file.path("..", "Output", "TablesRDS")
# FileID <- "fit"
# FileEncode <- "UTF-8"
# Delimiter <- ","
# HeaderRows <- 0
```

# Read Imported Solisense

```{r read locally stored metadata from rds}
LIFT445_0 <- read.csv(file = file.path("..", "Data", "RawData", "SolisenseCurveData", "PICO_202112201453_SySl1035_445_data_dark.csv"))
LIFT445_0<-LIFT445_0 %>% 
  rename(DataPt=X....) %>% 
  rename(Time_us=X) %>% 
  rename(EX=X.1) %>% 
  rename(EM=X.2) %>% 
  rename(Fit=X.3) %>% 
  rename(PAR = X.4) %>% 
  select(-c(X.5))
LIFT445_0 = LIFT445_0[-1:-15,]
LIFT445_0[is.na(LIFT445_0)] <- 0
LIFT445_0$Ex_WL <- 445

LIFT445_80 <- read.csv(file = file.path("..", "Data", "RawData", "SolisenseCurveData", "PICO_202112201453_SySl1035_445_data_light80.csv"))
LIFT445_80<-LIFT445_80 %>% 
  rename(DataPt=X....) %>% 
  rename(Time_us=X) %>% 
  rename(EX=X.1) %>% 
  rename(EM=X.2) %>% 
  rename(Fit=X.3) %>% 
  rename(PAR = X.4) %>% 
  select(-c(X.5))
LIFT445_80 = LIFT445_80[-1:-15,]
LIFT445_80[is.na(LIFT445_80)] <- 80
LIFT445_80$Ex_WL <- 445

LIFT590_0 <- read.csv(file = file.path("..", "Data", "RawData", "SolisenseCurveData", "PICO_202112201547_SySl1035_590_data_dark.csv"))
LIFT590_0<-LIFT590_0 %>% 
  rename(DataPt=X....) %>% 
  rename(Time_us=X) %>% 
  rename(EX=X.1) %>% 
  rename(EM=X.2) %>% 
  rename(Fit=X.3) %>% 
  rename(PAR = X.4) %>% 
  select(-c(X.5))
LIFT590_0 = LIFT590_0[-1:-15,]
LIFT590_0[is.na(LIFT590_0)] <- 0
LIFT590_0$Ex_WL <- 590

LIFT590_80 <- read.csv(file = file.path("..", "Data", "RawData", "SolisenseCurveData", "PICO_202112201547_SySl1035_590_data_light80.csv"))
LIFT590_80<-LIFT590_80 %>% 
  rename(DataPt=X....) %>% 
  rename(Time_us=X) %>% 
  rename(EX=X.1) %>% 
  rename(EM=X.2) %>% 
  rename(Fit=X.3) %>% 
  rename(PAR = X.4) %>% 
  select(-c(X.5))
LIFT590_80 = LIFT590_80[-1:-15,]
LIFT590_80[is.na(LIFT590_80)] <- 80
LIFT590_80$Ex_WL <- 590


LIFT<-rbind(LIFT590_80, LIFT590_0, LIFT445_80, LIFT445_0)
rm(LIFT590_80, LIFT590_0, LIFT445_80, LIFT445_0)

LIFT$SampleID <- "SySl1035"
LIFT$ObsDate <- 20211220

LIFT<-LIFT %>% 
  mutate(ObsDate=as.Date(ObsDate)) %>% 
  mutate(DataPt=as.double(DataPt)) %>% 
  mutate(Time_us=as.double(Time_us)) %>% 
  mutate(EX=as.double(EX)) %>% 
  mutate(EM=as.double(EM)) %>% 
  mutate(Fit=as.double(Fit)) 
```

# Merge LIFT data with MetaData

```{r combine Solisense and MetaData catalog, warning = FALSE, echo=FALSE}
LIFTMeta <- LIFT %>%
  left_join(., CultureCatalog, by = c("SampleID" = "SampleID"))

rm(LIFT)
```

```{r}
LIFTMeta$facetsActinicPAR = factor(LIFTMeta$O2, labels = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"))
LIFTMeta$facetsExcitation = factor(LIFTMeta$WL, labels = c("Excitation~(nm)"))
```


# Create preliminary plot

```{r fig.height = 4.5, fig.width = 8, warning = FALSE}
data_textA <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c('A'))

arrowdf1 <- tibble(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0), Ex_WL  = c(445), Strain = "PE-rich_048")
arrowdf2 <- tibble(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain = "PE-rich_048")

data_textSat <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0, 80), Ex_WL  = c(590), Strain  = c("PE-rich_048"), label = c('Saturation'))
data_textRel <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0, 80), Ex_WL  = c(590), Strain  = c("PE-rich_048"), label = c('Relaxation'))
data_textSat1 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0, 80), Ex_WL  = c(590), Strain  = c("PE-rich_048"), label = c('(~250 µs)'))
data_textRel1 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0, 80), Ex_WL  = c(590), Strain  = c("PE-rich_048"), label = c('(~250-50000 µs)'))


data_textTao <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c('italic(\u03C4)[1] - italic(\u03C4)[3]'))
data_textTaop <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c('italic(\u03C4)[1] - italic(\u03C4)[3]'))

data_textFm <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("italic(F)[m]"))
data_textFmp <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("italic(F)[m]"))

# data_textF0 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("F[0]"))
data_textF0 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("italic(F)[0]"))

data_textF <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("italic(F)[]"))
# data_textF <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("F"))

data_textPrime <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("~'/'"))
data_textPrime2 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("~'/'"))
data_textPrime3 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("~'/'"))
data_textPrime4 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("~'/'"))
data_textPrime5 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("~'/'"))

data_textSig <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c('\u03C3[PSII]'))
data_textSigp <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(80), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c('\u03C3[PSII]'))

# lab1=c(expression("PC-rich_056"), expression("PC-rich_077"), expression("PE-rich_048"), expression("PE-rich_127"))
# lab2=c(expression("8 h"), expression("12 h"), expression("16 h"), expression("24 h"))
# lab3=c(expression("30 µE"), expression("90 µE"), expression("180 µE"), expression("300 µE"), expression("900 µE"))


PlotA<-LIFTMeta %>%
  filter(Time_us<1000) %>% 
  ggplot() +
  #geom_point(aes(x = Time_us, y = EX),  colour = "brown4", alpha = 0.8, size = 1, show.legend = F) +
  geom_point(aes(x = Time_us, y = EM),  colour = "brown1", alpha = 0.8, size = 2, show.legend = F) +
  geom_line(aes(x = Time_us, y = Fit),  colour = "blue", alpha = 0.7, size = 0.7, show.legend = F) +
  geom_vline(xintercept = 250, linetype="dashed", col="black", lwd=0.2) +
  
  geom_text(data=data_textA, aes(x=950, y=500, label=label), size=4.5) +
  
  geom_text(data=data_textSat, aes(x=100, y=500, label=label), size=3.5) +
  geom_text(data=data_textRel, aes(x=500, y=500, label=label), size=3.5) +
  geom_text(data=data_textSat1, aes(x=100, y=210, label=label), size=3.5) +
  geom_text(data=data_textRel1, aes(x=500, y=210, label=label), size=3.5) +
  
  geom_text(data=data_textTao, aes(x=400, y=400, label=label), size=3.5, parse = TRUE) +
  geom_text(data=data_textTaop, aes(x=450, y=450, label=label), size=3.5, parse = TRUE) +
  
  geom_text(data=data_textFm, aes(x=200, y=500, label=label), size=3.5, parse = TRUE) +
  geom_text(data=data_textFmp, aes(x=200, y=550, label=label), size=3.5, parse = TRUE) +
  
  geom_text(data = data_textF0, aes(x = 50, y = 150, label = label), size = 3.5, parse = TRUE) +
  #geom_text(data=data_textF0, aes(x=50, y=100, label=expression(F[0])), size=3.5, parse = TRUE) +
  geom_text(data = data_textF, aes(x=50, y=200, label=label), size=3.5, parse = TRUE) +

  geom_text(data = data_textPrime, aes(x=240, y=565, label=label), size=2.5, parse = TRUE) +
  geom_text(data = data_textPrime2, aes(x=75, y=220, label=label), size=2.5, parse = TRUE) +
  geom_text(data = data_textPrime3, aes(x=120, y=460, label=label), size=2.5, parse = TRUE) +
  geom_text(data = data_textPrime4, aes(x=425, y=460, label=label), size=2.5, parse = TRUE) +
  geom_text(data = data_textPrime5, aes(x=540, y=460, label=label), size=2.5, parse = TRUE) +
  
  geom_text(data=data_textSig, aes(x=100, y=400, label=label), size=3.5, parse = TRUE) +
  geom_text(data=data_textSigp, aes(x=60, y=450, label=label), size=3.5, parse = TRUE) +
  
  geom_segment(data = arrowdf1, aes(x = -5, xend = 150, y = 230, yend = 360),
               colour = "black", size = 0.5, alpha=0.9, arrow = arrow(ends="both", type = "closed", length=unit(0.1, 'cm'))) +
  geom_segment(data = arrowdf2, aes(x = -10, xend = 150, y = 260, yend = 450),
               colour = "black", size = 0.5, alpha=0.9, arrow = arrow(ends="both", type = "closed", length=unit(0.1, 'cm'))) +

  #scale_colour_discrete(type=c("seagreen4", "palegreen3", "brown1", "brown4"), name="", labels = lab1) +
  # scale_y_continuous(breaks=seq(0, 2000, by = 500)) +
  # coord_cartesian(ylim = c(0, 2500)) +
  #annotate("text", x = 50, y = 100, label = expression(F[0]), size = 3.5, data = data_textF0) +
  #annotate("text", x = 1, y = 1, label = "\u03C4[PSII]", parse = TRUE) +
  labs(y = "Fluorescence yield", x = "Elapsed time (µs)") +
  ggh4x::facet_nested(cols = vars(facetsActinicPAR, PAR), rows = vars(facetsExcitation, Ex_WL), labeller = label_parsed, scales="free_y") +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.96),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=11))
PlotA
```

# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_LIFT_1",".png",sep = "")), height=4.5, width= 7,  dpi = 300, limitsize = TRUE)
```



```{r}
#SolFitsMetaLRC$facetsActinicPAR = factor(SolFitsMetaLRC$O2, labels = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"))
SolFitsMetaLRC$facetsExcitation = factor(SolFitsMetaLRC$WL, labels = c("Excitation~(nm)"))
```

```{r fig.height = 4, fig.width = 8, warning = FALSE}
data_textB <- data.frame(facetsExcitation  = c("Excitation~(nm)"), Ex_WL = c("445"), label = c('B'))


PlotB<-SolFitsMetaLRC %>%  
  unnest(GRCplatt_Predict) %>% 
  filter(Strain == "BA48R") %>% 
  filter(Par_ue == 180) %>% 
  filter(Photoperiod == 16) %>% 
  filter(E_days == 7) %>% 
ggplot() +
  geom_point(aes(ActPARCorr, JVPSII_ETRqpOxbo_FoSig*100), colour = "brown1", alpha = 0.8, size = 2, show.legend = T) +
  geom_line(aes(ActPARCorr, .fitted*100), colour = "blue", linetype = "solid", size = 0.4) +
  
  geom_text(data=data_textB, aes(x=800, y=450, label=label), size=4.5) +
  labs(y = ""~italic(JV)~""["PSII"]*" ("~10^18~""~e^-~""~L^-1~""~s^-1~")", x = "Actinic PAR ( µmol photons "~m^-2~""~s^-1~")") +
  

  ggh4x::facet_nested(rows = vars(facetsExcitation, Ex_WL), labeller = label_parsed) +
  theme_bw() +
  theme(panel.grid.minor = element_blank(),
        panel.grid.major = element_blank(),
        axis.text = element_text(size=12),
        axis.title = element_text(size=16),
        strip.background = element_rect(fill="white"),
        strip.text = element_text(size=12),
        axis.title.y = element_text(margin=margin(r=10)),
        axis.title.x = element_text(margin=margin(t=10)),
        legend.background = element_rect(fill="transparent"),
        legend.position = c(0.12,0.96),
        legend.key.height= unit(0.005, 'cm'),
        legend.spacing.x = unit(0.01, 'cm'),
        legend.text = element_text(size=11))
PlotB
```
# Merge two plots into one with panel A and B

```{r Final Plot arrange, warning = FALSE, fig.height = 8, fig.width = 8}
ss<-ggarrange(PlotA,PlotB,
          ncol = 1, nrow = 2) %>% 
  ggsave(file = file.path(FigPath, paste("Fig_LIFT",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```

# Save plot 

```{r save plot}
#ggsave(file = file.path(FigPath, paste("Fig_LIFT",".png",sep = "")), height=9, width= 7,  dpi = 300, limitsize = TRUE)
```


# Save rds for further analysis

```{r save rds}
# saveRDS(SolFitsTrimMetaClean, file.path(DataOut, paste(Project, "Imported_SolisenseLight1.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
# 
# saveRDS(SolFitsTrimMetaDarkafterLight, file.path(DataOut, paste(Project, "Imported_SolisenseDarkafterLight1.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# Variable names used in Data Dictionary

```{r}
# colnames(SolFitsTrimMetaClean)
```




--------------------------------------------------------------------------------------------------------------------------

Oxborough & Baker 1997 for Fo'

Oxborough, K., & Baker, N. R. (1997). Resolving chlorophyll a fluorescence images of photosynthetic efficiency into photochemical and non-photochemical components–calculation of qP and Fv-/Fm-; without measuring Fo. Photosynthesis research, 54, 135-142.

Oxborough, K., & Baker, N. R. (1997). An instrument capable of imaging chlorophyll a fluorescence from intact leaves at very low irradiance and at cellular and subcellular levels of organization. Plant, Cell & Environment, 20(12), 1473-1483.

Oxborough, K., Moore, C. M., Suggett, D. J., Lawson, T., Chan, H. G., & Geider, R. J. (2012). Direct estimation of functional PSII reaction center concentration and PSII electron flux on a volume basis: a new approach to the analysis of Fast Repetition Rate fluorometry (FRRf) data. Limnology and Oceanography: Methods, 10(3), 142-154.

Suggett, D. J., Moore, C. M., Oxborough, K., & Geider, R. J. (2006). Fast repetition rate (FRR) chlorophyll a fluorescence induction measurements. West Molesey: Chelsea Technologies Group, 1-53.




Berge, J., Grant, S., Bjørgum, R., Cohen, J. H., McKee, D., Johnsen, G., Zolich, A., Kopec, T. P., Vogedes, D. L., UiT The Arctic University of Norway (2021).Time series (2017) of irradiance in the PAR (photosynthetically active radiation) region measured under the dome of a light observatory in the Arctic  (Ny-Ålesund, Svalbard, Norway) derived from an USSIMO spectroradiometer [Data set]. Norstore. https://doi.org/10.11582/2021.00040

https://archive.norstore.no/pages/public/datasetDetail.jsf?id=10.11582/2021.00040

PAR is approximated as an integral of micromolespersec=(uirr/(h*c/(lambda*1e-9)))/microavo for wavelengths(lambda) in range from 400 to 700nm, where: uirr = USSIMO irradiance for wavelength equal to lambda, h=6.63e-34 [Js], c=3.00e+08 [m/s], microavo=6.022e17.





Fast Repetition Rate fluorometry (FRRf, Kolber et al. 1998) 

σPSII - Effective absorption cross section of PSII photochemistry in darkness -> A2 (quanta)-1 or m2
ρ - Connectivity between PSII reaction centres in darkness

σPSII′ - Effective absorption cross section of PSII photochemistry under actinic light -> A2 (quanta)-1 or m2
ρ′ - Connectivity between PSII reaction centres under actinic light

TauPSII - Minimum turnover time of PSII photochemistry -> s-1

F0 or F0’ (Minimum fluorescence in darkness or Minimum fluorescence under actinic light)
Fm or Fm’ (Maximum fluorescence in darkness or Maximum fluorescence under actinic light)
F’ (or Fs; Steady state fluorescence at any point)
Fv = Fm-F0 (Variable fluorescence in darkness)
Fv’ = Fm’-F0’ (Variable fluorescence under actinic light)
Fq′ = (Fm′ - F′) (Difference between Fm′ and F′)

Fv/Fm = (Fm-F0)/Fm (The maximum PSII quantum yield/Maximum photochemical efficiency)
Fv’/Fm’ = (Fm’- F0’)/Fm’ (Maximum PSII efficiency under actinic light)

ΦPSII = (Fm’- F’)/Fm’ = Fq′/Fm′ (Photochemical efficiency under actinic light)

qP = (Fm’- F’)/(Fm’-F0’) = (Fm′ - F′)/Fv′ = Fq′/Fv′ (PSII efficiency factor under actinic light; photochemical quenching coefficient) 

NPQ =(Fm-Fm’)/Fm’ (Non-photochemical quenching coefficien)


ETR = PPFD * aPSII * PSII photochemical efficiency (ΦPSII)

ETR^RCII = PPFD * σPSII * Fq′/Fm′ (or ΦPSII) * 21.683

ETR^chl = PPFD * σPSII * n PSII * Fq′/Fm′ (or ΦPSII) * 21.683


FRR fluorescence provides a direct measure of light absorption per unit PSII reaction centres (σPSII).

ETR, called the relative electron transport rate, is the product of the effective photochemical yield of
PSII (ΦPSII) and photosynthetic photon flux density

ETR^RCII(chl) - RCII (Chlorophyll a)-normalised rate of electron transfer by PSII -> mol e- g chla-1 h-1

ETR^chl is the chlorophylla-specific rate of electron transfer (mol e- mol chla-1 h-1 ).

PPFD (=E) - Photosynthetically active photon flux density -> μmol m-2 s-1

a^chlPSII - a^chl only used for PSII photochemistry -> m2 mg chla-1

(factor 21.683 converts seconds to hours, μmol e- to mol e- and A2 quanta-1 to m2 mol RCII-1)

nPSII - photosynthetic unit size of PSII

JVPSII - PSII flux per unit volume -> electrons m–3 s–1

[RCII] - concentration of functional PS II reaction centers -> m-3

aLHII - LHII (light harvesting complex II) absorption coefficient -> m-1


```{r example of different labels on plot}

# data_textF0 <- data.frame(facetsActinicPAR  = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"), facetsExcitation  = c("Excitation~(nm)"), PAR  = c(0), Ex_WL  = c(445), Strain  = c("PE-rich_048"), label = c("italic(F)[0]^{-1}"))

# data_textF0 <- data.frame(facetsActinicPAR = c("Actinic~PAR~(µmol~photons~m^{-2}~s^{-1})"),
#                           facetsExcitation = c("Excitation~(nm)"),
#                           PAR = c(0),
#                           Ex_WL = c(445),
#                           Strain = c("PE-rich_048"),
#                           label = c("~\"''\""))
# 
# LIFTMeta %>%
#   filter(Time_us < 1000) %>%
#   ggplot() +
#   geom_point(aes(x = Time_us, y = EM), colour = "brown1", alpha = 0.8, size = 2, show.legend = FALSE) +
#   geom_text(data = data_textF0, aes(x = 50, y = 100, label = label), size = 3.5, parse = TRUE) +
#   ggh4x::facet_nested(cols = vars(facetsActinicPAR, PAR), rows = vars(facetsExcitation, Ex_WL), labeller = label_parsed, scales = "free_y") +
#   theme_bw()

```
