---
title: "Import_PigmentData"
author:
- Naaman M. Omar 
- Sylwia Sliwinska-Wilczewska
- Douglas A. Campbell
date: "`r format(Sys.Date())`"
output:
bookdown::html_document2:
    code_folding: show
    keep_md: yes
    toc: TRUE
    toc_float: TRUE
    toc_depth: 6
    fig_caption: yes
bibliography: BalticPhotoperiod.bib
csl: plos-one.csl
editor_options: 
  markdown: 
    wrap: 72
---

# Set Chunk Options

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
knitr::opts_chunk$set(fig.path='Figs/')
```

# Introduction

Import_PigmentData.Rmd imports: PAMAS files from Data/RawData/PAMASData.zip folder; and ...

and stored in Data/ImportedData/ImportedPigmentData folder as: 
Baltic_Photoperiod_Imported_PigmentData.Rds

# Load Libraries and set Project Variables

```{r load libraries}
library(kableExtra)
library(tidyverse)
library(lubridate)
library(stringr)
library(broom)
library(knitr)
library(OneR)
library(zoo)
library(strucchange)
library(dplyr)
library(magrittr)
library(googledrive)
library(googlesheets4)
library(readxl)
```

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataOut <- file.path("..", "Data", "ImportedData", "ImportedPigmentsData")
#DataIn <- file.path("..", "Data", "RawData", "PamasData", fsep = .Platform$file.sep)

PlotsPath <- file.path("..", "Output", "Plots")
RDSPlotPath <- file.path("..", "Output", "PlotsRDS")
RDSTablePath <- file.path("..", "Output", "TablesRDS")
```

# IMPORT PAMAS CORRELATION DATA

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataIn <- file.path("..", "Data", "RawData", "PAMAS", fsep = .Platform$file.sep)

FileID <- "PAMAS"

FileEncode <- "UTF-8" 
HeaderRows <- 9
Delimiter <- "\t"
```

# List files in the extracted folder 

```{r}
CountFiles <- list.files(path = DataIn, pattern = FileID, full.names = TRUE)
CountFiles
unique(duplicated(CountFiles))
```

```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
#design choice 2 file reading functions or add a filetype variable to a single function

read.delim_plus <- function(flnm, file_encode, delimiter, header_rows){read.delim(flnm, fileEncoding = file_encode, sep = delimiter,  skip = header_rows, row.names = NULL) %>%
    mutate(filename = flnm, cdatetime = ymd_hms(file.info(flnm)$ctime))
}
```

```{r read Pamas file}

CountTidy <- CountFiles %>%
  map_df(~read.delim_plus(flnm =., file_encode = FileEncode, delimiter = Delimiter, header_rows = HeaderRows))
```


```{r tidy CountTidy}
CountTidy <- CountTidy %>% 
  mutate(filename = str_remove(string = filename, pattern = ".txt")) %>%
  mutate(filename = str_remove(string = filename, pattern = "../PAMAS/")) %>%
  separate(filename, into = c("FP1", "FP2", "Date", "Strain", "Dilution", "Device"), sep = "([\\/\\/\\_\\_\\_\\_])", remove = FALSE) 
```

# Remove a unrelated character (RawDa) in data frame column

```{r remove a unrelated character}
CountTidy$Date<-gsub("RawDa","",as.character(CountTidy$Date))

CountTidy<-CountTidy %>% 
  mutate(Date = as.double(`Date`)) %>%
  mutate(Date = ymd_hm(`Date`)) %>% 
  select(-c("FP1", "FP2"))
```


```{r tidy TargetPamasData}
#figur out how to read and rename these columns from the file rather than manually
NewNames <- c("PAMASDate", "Time", ">0.70",">0.80", ">0.90", ">1.00", ">1.20", ">1.50", ">2.00",">3.00", ">4.00", ">5.00", ">6.00", ">7.00", ">10.00", ">12.00",
">15.00",">20.00", "Filename", "Date","Strain", "Dilution", "Device", "cdatetime")

OldNames <- colnames(CountTidy)

PamasTidy <- CountTidy %>%
rename_with(~NewNames[which(OldNames == .x)], .cols = OldNames) %>%
  mutate(datetime = paste(PAMASDate, Time),
         datetime = mdy_hms(datetime))
```

```{r}
PamasTidy <- PamasTidy %>%
mutate(`S0.7` = as.numeric(`>0.70`) - as.numeric(`>0.80`),
       `S0.8` = as.numeric(`>0.80`) - as.numeric(`>0.90`),
       `S0.9` = as.numeric(`>0.90`) - as.numeric(`>1.00`),
       `S1.0` = as.numeric(`>1.00`) - as.numeric(`>1.20`),
       `S1.2` = as.numeric(`>1.20`) - as.numeric(`>1.50`),
       `S1.5` = as.numeric(`>1.50`) - as.numeric(`>2.00`),
       `S2.0` = as.numeric(`>2.00`) - as.numeric(`>3.00`),
       `S3.0` = as.numeric(`>3.00`) - as.numeric(`>4.00`),
       `S4.0` = as.numeric(`>4.00`) - as.numeric(`>5.00`),
       `S5.0` = as.numeric(`>5.00`) - as.numeric(`>6.00`),
       `S6.0` = as.numeric(`>6.00`) - as.numeric(`>7.00`),
       `S7.0` = as.numeric(`>7.00`) - as.numeric(`>10.00`),
       `S10.0` = as.numeric(`>10.00`) - as.numeric(`>12.00`),
       `S12.0` = as.numeric(`>12.00`) - as.numeric(`>15.00`),
       `S15.0` = as.numeric(`>15.00`) - as.numeric(`>20.00`),
       `S20.0` = as.numeric(`>20.00`))

PamasTidy <- PamasTidy %>%
  # select(Date, Time, Filename, SampleID, `S0.7`, `S0.8`, `S0.9`, `S1.0`, `S1.2`, `S1.5`, `S2.0`, `S3.0`, `S4.0`, `S5.0`, `S6.0`, `S7.0`, `S10.0`, `S12.0`, `S15.0`, `S20.0`) %>%
  pivot_longer(., cols = c("S0.7", "S0.8", "S0.9", "S1.0", "S1.2", "S1.5", "S2.0", "S3.0", "S4.0", "S5.0", "S6.0", "S7.0", "S10.0", "S12.0", "S15.0", "S20.0"), names_to = "CellSize_um", values_to = "Count") %>%
  mutate_at("CellSize_um", str_replace, "S", "") %>%
  mutate(CellSize_um = as.numeric(CellSize_um)) %>%
  group_by(CellSize_um, Strain, Dilution) %>%
  mutate(meanCount = mean(Count), 
         sdCount = sd(Count)) %>%
  ungroup() %>%
  select(c(PAMASDate, Filename, Date, Strain, Dilution, cdatetime, CellSize_um, Count, meanCount, sdCount))
```

```{r}
PamasTidy<-PamasTidy %>% 
  rename(ObsDate=Date) %>%
  rename(FilenamePAMAS=Filename) %>% 
  select(-c(cdatetime, PAMASDate))
```

# Create preliminary plot
```{r preliminary plot}
PamasTidy %>%
  mutate(meanCount104 = meanCount/10000) %>%
  mutate(sdCount104 = sdCount/10000) %>%
  filter(CellSize_um < 4) %>% 
  ggplot() +
  geom_point(aes(x = Dilution, y =meanCount104, label = Strain)) +
  geom_errorbar(aes(x = Dilution, ymin = meanCount104-sdCount104, ymax = meanCount104+sdCount104)) +
  labs(y = "Number of cells (N" ~10^4 ~mL^-1~")", x = "Culture concentration (mL)") +
  scale_y_continuous(breaks=seq(0, 12, by = 4)) +
  coord_cartesian(ylim = c (0, 12)) +
  ggh4x::facet_nested(rows = vars(CellSize_um), cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()
```
# Removed unnecessary files from the environment

```{r removed unnecessary files from the environment}
rm(CountTidy)
```

# Save rds for further analysis

```{r save rds}
# saveRDS(PamasTidy, file.path(DataOut, paste(Project, "Imported_PamasData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# IMPORT MD PICO CORRELATION DATA

```{r set project variables}
Project <- "Baltic_Photoperiod"
DataIn <- file.path("..", "Data", "RawData", "MDPicoData", fsep = .Platform$file.sep)

FileEncode <- "UTF-8" 
Delimiter <- ","
HeaderRows <- 0
FileID <- "ExperimentSummaryData"
```

# MDPico catalog 

```{r load local metadatacatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
MDPicoCatalog <- read_sheet("https://docs.google.com/spreadsheets/d/1xDZ5eiCFgqJ-AgO7jhCSKS7oyO39KpwjZm0UpdP2p2c/edit#gid=0") %>%
  mutate(Date = ymd_hm(`Date`)) %>%
  separate(Date, into = c("Date_count", "Time_count"), sep = " ", remove = FALSE) %>%
  mutate(Date_count = ymd(`Date_count`)) 
```

```{r}
CountFiles <- list.files(path = DataIn, pattern = FileID, full.names = TRUE)
CountFiles
unique(duplicated(CountFiles))
```

```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
#design choice 2 file reading functions or add a filetype variable to a single function

read.delim_plus <- function(flnm, file_encode, delimiter, header_rows){read.delim(flnm, fileEncoding = file_encode, sep = delimiter,  skip = header_rows, row.names = NULL) %>% mutate(filename = flnm, cdatetime = ymd_hms(file.info(flnm)$ctime))
}
```

purrr::map to read all files
```{r read MDPico file}
CountTidy <- CountFiles %>%
  map_df(~read.delim_plus(flnm =., file_encode = FileEncode, delimiter = Delimiter, header_rows = HeaderRows))
```

```{r tidy CountTidy}

CountTidy <- CountTidy %>% 
  #filter(!grepl("----", DATE)) %>% # remove rows with "----"
  select(-c("Concentration", "Group", "Compound")) %>% # remove superfluous columns
  mutate(filename = str_remove(string = filename, pattern = ".csv")) %>%
  mutate(filename = str_remove(string = filename, pattern = "../MDPico/")) %>%
  separate(filename, into = c("fp0", "fp1", "fp2", "Method", "ObsDate", "Project", "Initials",  "PlateNr", "Correlation", "Methods", "Organism"), sep = "([\\/\\/\\_\\_\\_\\_])", remove = FALSE) %>%
  mutate(cdatetime = ymd_hms(cdatetime)) %>%
  mutate(ObsDate = ymd_hm(ObsDate)) %>% 
  select(-c(fp0, fp1, fp2, Method, Project))
```

```{r}
CountMeta<- CountTidy %>%
  mutate(PlateNr = as.double(PlateNr)) %>%
  left_join(., MDPicoCatalog, by = c("Well.Name" = "WellNumber", "PlateNr" = "PlateNumber"))
```

```{r}
CountMeta <- CountMeta %>%
  mutate(culture_inocul_L = as.double(culture_inocul_L)) %>%
  mutate(CapAreaPercentage = as.double(CapAreaPercentage)) %>%
  mutate(cellsml = (`Cell.Count` * (0.001/culture_inocul_L)) /(CapAreaPercentage/100)) %>%
group_by(Date, Strain, Dilution) %>%

summarize(Well.Name, Cell.Count, filename, ObsDate, PlateNr, PlateID, Strain,Dilution,Date, Date_count, Time_count, media_inocul_L, culture_inocul_L, CapAreaPercentage, TotArea_mm2, CapArea_mm2, cellsml, 
          meancellsml = mean(cellsml), 
          sdcellsml = sd(cellsml)) %>%
ungroup() 


CountMeta <- CountMeta %>%
  rename(CellCount=Cell.Count) %>%
  rename(WellName=Well.Name) %>%
  rename(MolDev_FileName=filename) %>% 
  rename(DateCollect=Date_count) %>% 
  rename(TimeCollect=Time_count) %>% 
  select(-c(TotArea_mm2, CapArea_mm2, Date))
```

# Create preliminary plot

```{r}
CountMeta %>%
  ggplot() +
  geom_point(aes(x = Dilution, y = meancellsml)) +
  # geom_errorbar(aes(x = E_days, ymin = meancellsml107-sdcellsml107, ymax = meancellsml107+sdcellsml107)) +
  labs(y = "Number of cells/mL", x = "Time (d)") +
  ggh4x::facet_nested(cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, WL = label_both, Photoperiod = label_both, Par_ue = label_both)) +
  theme_bw()
```
# Removed unnecessary files from the environment

```{r removed unnecessary files from the environment}
rm(CountTidy, MDPicoCatalog)
```

# Save rds for further analysis

```{r save rds}
# saveRDS(CountMeta, file.path(DataOut, paste(Project, "Imported_MDPicoData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# IMPORT PIGMENTS CORRELATION DATA FROM CLARIOSTAR (FILTERS)

```{r}
Project <- "Baltic_Photoperiod"
#DataIn <- file.path("..", "Data", "RawData", "MDPicoData", fsep = .Platform$file.sep) 
FileEncode <- "UTF-8" 
Delimiter <- ","
HeaderRows <- 0
```

# Load Pigment catalog

```{r load local metadatacatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
PigmentData <- read_sheet("https://docs.google.com/spreadsheets/d/1EvogE5pFlGT9H304E3dqXKwh26dWI9r_snSPhZCHWiU/edit#gid=0") %>%
  mutate(Date = as.numeric(Date)) %>%
  mutate(Date = ymd(`Date`)) %>%
  mutate(MeasDate = ymd(`MeasDate`))
```

# Read MetaData

```{r read locally stored metadata from rds}
CultureCatalog <- readRDS(file = file.path("..", "Data", "ImportedData", "ImportedMetaData", "CultureCatalog.Rds"))

CultureCatalog<-CultureCatalog %>% 
  select(-c(PrimaryOperator, Temp_c, ExpCul, ExpStartTime, O2_Category, Optode, OptodeCh, OptodeMeasure))
```

```{r}
PigmentsClario <- PigmentData %>%
  left_join(., CultureCatalog, by = c("CultureID" = "SampleID"))
```

```{r data read adds filename and cdate, warning=FALSE, message=FALSE, echo=FALSE}
PigmentsClario <- PigmentsClario %>%
  mutate(OD480 = as.double(OD480), OD565 = as.double(OD565), OD620 = as.double(OD620), OD650 = as.double(OD650),OD665 = as.double(OD665), OD750 = as.double(OD750)) %>%
  mutate(Vacetone_mL = as.double(Vacetone_mL)) %>%
  mutate(Vculture_mL = as.double(Vculture_mL)) %>%
  
  mutate(Chla_ugmL = case_when(Analysis == 'ChlaCar' ~ 11.236*(OD665-OD750)*Vacetone_mL/Vculture_mL)) %>%
  mutate(Car_ugmL = case_when(Analysis == 'ChlaCar' ~  4*(OD480-OD750)*Vacetone_mL/Vculture_mL)) %>%
  mutate(PC_ugmL = case_when(Analysis == 'Phyco' ~ (((OD620-OD750)-0.7*(OD650-OD750))/7.38)*(Vacetone_mL/Vculture_mL)*1000)) %>%
  mutate(APC_ugmL = case_when(Analysis == 'Phyco' ~ (((OD650-OD750)-0.19*(OD620-OD750))/5.65)*(Vacetone_mL/Vculture_mL)*1000)) %>%
  mutate(PE_ugmL = case_when(Analysis == 'Phyco' ~  (((OD565-OD750)*1000-2.8*PC_ugmL-1.34*APC_ugmL)/12.7)*(Vacetone_mL/Vculture_mL))) %>%
  
  mutate(CarChlaRatio = Car_ugmL/Chla_ugmL) %>%
  mutate(PhycoTot = PC_ugmL + APC_ugmL + PE_ugmL) %>%
  mutate(PCPERatio = PC_ugmL/PE_ugmL) %>%
  mutate(PEPCRatio = PE_ugmL/PC_ugmL) %>%
  
  mutate(PhycoChlaRatio = PhycoTot/Chla_ugmL) %>%
  mutate(PhycoCarRatio = PhycoTot/Car_ugmL)
```

```{r}
PigmentsClario <- PigmentsClario %>%
group_by(CultureID, Date, Analysis) %>%
mutate(meanChla_ugmL = mean(Chla_ugmL), meanCar_ugmL = mean(Car_ugmL), meanCarChlaRatio = mean(CarChlaRatio), meanPC_ugmL = mean(PC_ugmL), meanAPC_ugmL = mean(APC_ugmL), meanPE_ugmL = mean(PE_ugmL), meanPhycoTot = mean(PhycoTot), meanPCPERatio = mean(PCPERatio), meanPEPCRatio = mean(PEPCRatio), meanPhycoChlaRatio = mean(PhycoChlaRatio), meanPhycoCarRatio = mean(PhycoCarRatio), sdChla_ugmL = sd(Chla_ugmL), sdCar_ugmL = sd(Car_ugmL), sdCarChlaRatio = sd(CarChlaRatio), sdPC_ugmL = sd(PC_ugmL), sdAPC_ugmL = sd(APC_ugmL), sdPE_ugmL = sd(PE_ugmL), sdPhycoTot = sd(PhycoTot), sdPCPERatio = sd(PCPERatio), sdPEPCRatio = sd(PEPCRatio), sdPhycoChlaRatio = sd(PhycoChlaRatio), sdPhycoCarRatio = sd(PhycoCarRatio)) %>%
ungroup() %>%
  
select(c(PlateAb, WellAb, CultureID, Date, MeasDate, MeasTime, Analysis, Vculture_mL, Vacetone_mL, OD480, OD565, OD620, OD650, OD665, OD750, ClariostarFileName, Device, Run, Strain, ExpDate, Par_ue, Photoperiod, Tube, O2, WL, LightShape, ExpEndDate, PARPhotonDose_day, Chla_ugmL, Car_ugmL, CarChlaRatio, PC_ugmL, APC_ugmL, PE_ugmL, PhycoTot, PCPERatio, PEPCRatio, PhycoChlaRatio, PhycoCarRatio, meanChla_ugmL, meanCar_ugmL, meanCarChlaRatio, meanPC_ugmL, meanAPC_ugmL, meanPE_ugmL, meanPhycoTot, meanPCPERatio, meanPEPCRatio, meanPhycoChlaRatio, meanPhycoCarRatio, sdChla_ugmL, sdCar_ugmL, sdCarChlaRatio, sdPC_ugmL, sdAPC_ugmL, sdPE_ugmL, sdPhycoTot, sdPCPERatio, sdPEPCRatio, sdPhycoChlaRatio, sdPhycoCarRatio)) %>%

group_by(CultureID) %>%
  arrange(Date) %>%
  mutate(E_days = as.numeric((Date - ExpDate[1]))) %>%
ungroup()

# Designations:
# Date <- day when the sample was taken from the MultiCulti 
# ExpDate <- day indicating the start of the multiculti experiment

PigmentsClario<-PigmentsClario %>% 
  rename(SampleID=CultureID) %>% 
  rename(DateCollect=Date) %>% 
  rename(ObsDate=MeasDate) %>% 
  rename(ObsTime=MeasTime)
```

# Create Preliminary plot

```{r create preliminary plot}

PigmentsClario %>%
  ggplot() +
  geom_point(aes(x = E_days, y = meanChla_ugmL)) +
  #geom_errorbar(aes(x = E_days, ymin = meanChla_ugmL-sdChla_ugmL, ymax = meanChla_ugmL+sdChla_ugmL)) +
  labs(y = "Chl a content (µg" ~mL^-1~")", x = "Time (d)") +
  scale_x_continuous(breaks=seq(0, 14, by = 7)) +
  coord_cartesian(xlim = c (-1, 15)) +
  ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Strain, Photoperiod), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()
```

# Removed unnecessary files from the environment

```{r removed unnecessary files from the environment}
rm(PigmentData)
```

# Save rds for further analysis

```{r save rds}
# saveRDS(PigmentsClario, file.path(DataOut, paste(Project, "Imported_PigmentsClarioData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```

# IMPORT CLARIOSTAR CORRELATION DATA

```{r}
Project <- "Baltic_Photoperiod"

FileEncode <- "UTF-8" 
Delimiter <- ","
HeaderRows <- 0
```



# Load ClarioSTAR catalog

```{r load local metadatacatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()
MetaData <- read_sheet("https://docs.google.com/spreadsheets/d/1a318QMEFfB6F-eS4DC4y0hK9nXHYY6kpLOubl12z-as/edit#gid=0") %>%
  mutate(MeasDate = ymd(`MeasDate`))

```

```{r}
MetaDataAll <- MetaData %>%
  left_join(., CultureCatalog, by = c("CultureID" = "SampleID"))
```


```{r}
GrowthClario <- MetaDataAll %>%
mutate(OD750 = as.numeric(OD750), OD720 = as.numeric(OD720), OD680 = as.numeric(OD680)) %>%

group_by(CultureID, MeasDate) %>%
mutate(meanOD750 = mean(OD750), meanOD720 = mean(OD720), meanOD680 = mean(OD680), sdOD750 = sd(OD750), sdOD720 = sd(OD720), sdOD680 = sd(OD680)) %>% 
ungroup() %>%

select(c(PlateAb, WellAb, CultureID, MeasDate, MeasTime, Analysis, OD750, OD720, OD680, ClariostarFileName, Device, Run, Strain, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, Tube, O2, WL, LightShape, ExpEndDate, meanOD750, meanOD720, meanOD680, sdOD750, sdOD720, sdOD680)) %>%


group_by(CultureID) %>%
  arrange(MeasDate) %>%
  mutate(E_days = as.numeric((MeasDate - ExpDate[1]))) %>%
ungroup()

# Designations:
# E_days <- day of the experiment on which the sample was taken using R
# InnocDate <- day indicating the innoculation of the multiculti experiment
# ExpDate <- day indicating the start of the multiculti experiment

GrowthClario<-GrowthClario %>% 
  rename(ObsDate=MeasDate) %>% 
  rename(ObsTime=MeasTime)
```

# Create preliminary plot
```{r prelimplots}

GrowthClario %>%
  ggplot() +
  geom_point(aes(x = E_days, y = meanOD750)) +
  geom_errorbar(aes(x = E_days, ymin = meanOD750-sdOD750, ymax = meanOD750+sdOD750)) +
  labs(y = "Absorbance" ~ "("~OD[750]~")", x = "Time (d)") +
  ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Strain, Photoperiod), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```

From flowcytometer from Poland (BD Accuri)
```{r}
  
# GrowthClarioN <- GrowthClario %>%
#   mutate(OD750N = case_when(
#           Strain == 'BA77G' ~ 5766620.03*OD750+5146.44,
#          Strain == 'BA56G' ~ 815627.77*OD750-6499.89, 
#          Strain == 'BA48R' ~ 110516351.55*OD750-568505.87,
#          Strain == 'BA127R' ~ 124271003.22*OD750-1691760.02))

```


```{r}
# GrowthClarioN <- GrowthClarioN %>%
# mutate(OD750N = as.numeric(OD750N)) %>%
# 
# group_by(CultureID, MeasDate) %>%
# mutate(meanOD750N = mean(OD750N), 
#        sdOD750N = sd(OD750N)) %>% 
# ungroup() %>%
# 
# select(c(CultureID, MeasDate, Analysis, OD750, OD720, OD680, E_days, Run, Strain, ExpDate, Par_ue, Photoperiod, PARPhotonDose_day, Tube, O2, WL, LightShape, meanOD750, meanOD720, meanOD680, sdOD750, sdOD720, sdOD680, OD750N, meanOD750N, sdOD750N)) 
  
```

WW Photoperiod N by BDAccuri Plot
```{r fig.height = 6, fig.width = 8, echo = FALSE}

# GrowthClarioN %>%
#   ggplot() +
#   geom_point(aes(x = E_days, y = meanOD750N)) +
#   geom_errorbar(aes(x = E_days, ymin = meanOD750N-sdOD750N, ymax = meanOD750N+sdOD750N)) +
#   labs(y = "Number of cells (N" ~ ~mL^-1~")", x = "Time (d)") +
#   ggh4x::facet_nested(rows = vars(Par_ue), cols = vars(Strain, Photoperiod), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
#   theme_bw()
```



```{r}
colnames(GrowthClario)

GrowthClario<-GrowthClario %>% 
  rename(ObsDate=MeasDate) %>% 
  rename(ObsTime=MeasTime)
```


```{r}
# saveRDS(GrowthClario, file.path(DataOut, paste(Project, "ClarioAbGrowth.Rds", sep = "_"), fsep = .Platform$file.sep))
```





```{r}
Project <- "Baltic_Photoperiod"

FileEncode <- "UTF-8" 
Delimiter <- ","
HeaderRows <- 0
```


Load metadatacatalog
```{r load local metadatacatalog, message = FALSE, warning = FALSE, echo=FALSE}
gs4_deauth()

MetaData2 <- read_sheet("https://docs.google.com/spreadsheets/d/1cfyxO1bFSeEMlMnx1vAyuskk3Un_bqkE9-uUSc-jwhE/edit#gid=0") %>%
  mutate(MeasDate = ymd(`MeasDate`))
```

```{r}
GrowthClarioCorrelation <- MetaData2 %>%
mutate(OD750 = as.numeric(OD750), OD720 = as.numeric(OD720), OD680 = as.numeric(OD680)) %>%

group_by(Strain, MeasDate, Dilution) %>%
mutate(meanOD750 = mean(OD750), meanOD720 = mean(OD720), meanOD680 = mean(OD680), sdOD750 = sd(OD750), sdOD720 = sd(OD720), sdOD680 = sd(OD680)) %>% 
ungroup() %>%

select(c(PlateAb, WellAb, Strain, Dilution, MeasDate, MeasTime, Analysis, OD750, OD720, OD680, ClariostarFileName, Device, meanOD750, meanOD720, meanOD680, sdOD750, sdOD720, sdOD680)) 

# Designations:
# E_days <- day of the experiment on which the sample was taken using R
# ExpDate <- day indicating the start of the multiculti experiment

GrowthClarioCorrelation<-GrowthClarioCorrelation %>% 
  rename(ObsDate=MeasDate) %>% 
  rename(ObsTime=MeasTime)
```

Some examle of plot
```{r prelimplots}

GrowthClarioCorrelation %>%
  ggplot() +
  geom_point(aes(x = Dilution, y = meanOD750, label = Strain)) +
  geom_errorbar(aes(x = Dilution, ymin = meanOD750-sdOD750, ymax = meanOD750+sdOD750)) +
  labs(y = "Absorbance" ~ "("~OD[750]~")") +
  ggh4x::facet_nested(cols = vars(Strain), labeller = labeller(Ex_WL = label_both, strain = label_value, Par_ue = label_both, WL = label_both, Photoperiod = label_value)) +
  theme_bw()

```

# Removed unnecessary files from the environment

```{r removed unnecessary files from the environment}
rm(PigmentData)
```

# Save rds for further analysis

```{r save rds}
# saveRDS(PigmentsClario, file.path(DataOut, paste(Project, "Imported_PigmentsClarioData.Rds", sep = "_"), fsep = .Platform$file.sep), ascii = FALSE, version = NULL, compress = "xz", refhook = NULL)
```













